### 2023-03-18 NTIRE 2023 Efficient SR Challenge Factsheet/EfficientSR_factsheet.tex
init factsheet

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
% \usepackage[review]{cvpr}      % To produce the REVIEW version
\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage[shortlabels]{enumitem}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{NTIRE 2023 Efficient SR Challenge Factsheet\\-title of the contribution-}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

\section{Introduction}

This factsheet template is meant to structure the description of the contributions made by each participating team in the NTIRE 2023 challenge on efficient image super-resolution.

Ideally, all the aspects enumerated below should be addressed.
The provided information, the codes/executables and the achieved performance on the testing data are used to decide the awardees of the NTIRE 2023 challenge.

Reproducibility is a must and needs to be checked for the final test results in order to qualify for the NTIRE awards.

The main winners will be decided based on overall performance and a number of awards will go to novel, interesting solutions and to solutions that stand up as the best in a particular subcategory the judging committee will decided. Please check the competition webpage and forums for more details.

The winners, the awardees and the top ranking teams will be invited to co-author the NTIRE 2023 challenge report and to submit papers with their solutions to the NTIRE 2023 workshop. Detailed descriptions are much appreciated.

The factsheet, \href{https://github.com/ofsoundof/NTIRE2023_ESR}{source codes/executables}, trained models should be sent to \textbf{all of the NTIRE 2023 challenge organizers (Yawei Li, Yulun Zhang, and Radu Timofte)} by email.

\section{Email final submission guide}

\noindent To: {yawei.li@vision.ee.ethz.ch} \\ {yulun100@gmail.com} \\ {timofte.radu@gmail.com}\\
\noindent cc: your\_team\_members\\
Title: NTIRE 2023 Efficient SR Challenge - TEAM\_NAME - TEAM\_ID\\

To get your TEAM\_ID, please register at \href{https://docs.google.com/spreadsheets/d/1oekPThh5mq9qKax0hPZiQSHlqTjaoQa-IBfrQkwN7gk/edit?usp=sharing}{Google Sheet}. Please fill in your Team Name, Contact Person, and Contact Email in the first empty row from the top of sheet.
% 
Body contents should include:

\begin{enumerate}[a)]
\item team name

\item team leader's name and email address

\item rest of the team members

\item user names on NTIRE 2023 CodaLab competitions

\item Code, pretrained model, and factsheet download command, e.g. \texttt{git clone ...}, \texttt{wget ...}

\item Result download command, e.g. \texttt{wget ...}
\begin{itemize}
    \item Please provide different urls in e) and f)
\end{itemize}
\end{enumerate}

\noindent Factsheet must be a compiled pdf file together with a zip with .tex factsheet source files. Please provide a detailed explanation.

\section{Code Submission}

The code and trained models should be organized according to the \href{https://github.com/ofsoundof/NTIRE2023_ESR}{GitHub repository}. This code repository provides the basis to compare the various methods in the challenge. \textbf{Code scripts based on other repositories will not be accepted.} Specifically, you should follow the steps below.
\begin{enumerate}
    \item Git clone \href{https://github.com/ofsoundof/NTIRE2023_ESR}{the repository.}
    \item Put your model script under the \texttt{models} folder. Name your model script as \texttt{[Your\_Team\_ID]\_[Your\_Model\_Name].py}.
    \item Put your pretrained model under the \texttt{model\_zoo} folder. Name your model checkpoint as \texttt{[Your\_Team\_ID]\_[Your\_Model\_Name].[pth or pt or ckpt]}
    \item Modify \texttt{model\_path} in \texttt{test\_demo.py}. Modify the imported models.
    \item \texttt{python test\_demo.py}
\end{enumerate}
Please send us the command to download your code, e.g. \texttt{git clone [Your repository link]}
When submitting the code, please remove the LR and SR images in \texttt{data} folder to save the bandwidth.

\section{Factsheet Information}

The factsheet should contain the following information. Most importantly, you should describe your method in detail. The training strategy (optimization method, learning rate schedule, and other parameters such as batch size, and patch size) and training data (information about the additional trainning data) should also be explained in detail.

\subsection{Team details}

\begin{itemize}
\item Team name                                  
\item Team leader name                           
\item Team leader address, phone number, and email 
\item Rest of the team members        
\item Team website URL (if any)                   
\item Affiliation
\item Affiliation of the team and/or team members with NTIRE 2023 sponsors (check the workshop website)
\item User names and entries on the NTIRE 2023 Codalab competitions (development/validation and testing phases)
\item Best scoring entries of the team during development/validation phase
\item Link to the codes/executables of the solution(s)
\end{itemize}

\subsection{Method details}

You should describe your proposed solution in detail. This part is equivalent to the methodology part of a conference paper submission. The description should cover the following details.

\begin{itemize}
\item General method description (How is the network designed.)                                
%\item Description of the particularities of the solutions deployed for each of the challenge competitions or tracks
\item Representative image / diagram / pipeline of the method(s)  
\item Training strategy
\item Experimental results
\item References                                               
\end{itemize}

Additionally, you can refer to the following items to detail your description.
\begin{itemize}
\item Total method complexity (number of parameters, FLOPs, GPU memory consumption, number of activations, runtime)
\item Which pre-trained or external methods / models have been used (for any stage, if any) 
\item Which additional data has been used in addition to the provided NTIRE training and validation data (at any stage, if any) 
\item Training description
\item Testing description
\item Quantitative and qualitative advantages of the proposed solution
\item Results of the comparison to other approaches (if any)
\item Results on other benchmarks (if any)
\item Novelty degree of the solution and if it has been previously published
\item It is OK if the proposed solution is based on other works (papers, reports, Internet sources (links), etc). It is ethically wrong and a misconduct if you are not properly giving credits and hide this information.
\end{itemize}

% \section{Technical details}
% \begin{itemize}
% \item Language and implementation details (including platform, memory, parallelization requirements)
% \item Human effort required for implementation, training and validation?
% \item Training/testing time? Runtime at test per image (\textbf{including ensemble}).
% \item Comment the robustness and generality of the proposed solution(s)? 
% % Is it easy to deploy it for other sets of downscaling operators? 
% \item Comment the efficiency of the proposed solution(s)?
% \end{itemize}

\section{Other details}
\begin{itemize}
\item Planned submission of a solution(s) description paper at NTIRE 2023 workshop.
\item General comments and impressions of the NTIRE 2023 challenge. 
\item What do you expect from a new challenge in image restoration, enhancement and manipulation?
\item Other comments: encountered difficulties, fairness of the challenge, proposed subcategories, proposed evaluation method(s), etc.
\end{itemize}

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2023-03-18 NTIRE 2023 RTSR Factsheet/main.tex
init factsheet

%% Factsheet template for AIM 2022 challenge
%% 
%%

\documentclass{article}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{colortbl, color, xcolor}

\title{NTIRE 2023 Real-Time Super-Resolution}

%%% Makre sure your teamname is short and does not contain special characters. It can also be the name of your method e.g. CompactSRNet - be more creative than use :)

%%% Add Your names and affiliations.
\author{\textcolor{red}{Your Teamname Here}\\
\textcolor{red}{Your names}\thanks{\textcolor{blue}{Affiliations}}\\
}

\begin{document}

\maketitle

This factsheet template is meant to structure the description of the contributions made by each participating team in the NTIRE 2023 Real-Time Super-Resolution Challenge.
%
The provided information, the codes/executables and the achieved performance on the testing data are used to decide the awardees of the NTIRE 2023 Real-Time Super-Resolution Challenge.

\begin{enumerate}
    \item The models will be benchmarked as indicated in \url{https://github.com/eduardzamfir/NTIRE23-RTSR#evaluation-of-your-submission}.
    \item The test set is similar to the validation set, including only 4K native images. Reproducibility is a must. \textbf{We will only run and benchmark the models, we will not release or open-source them.} Open sourcing the solution is a must to receive the prizes, up to the team.
    \item The winners, the awardees and the top ranking teams will be invited to co-author the NTIRE 2023 Real-Time Super-Resolution Challenge report and to submit papers with their solutions to the NTIRE 2023 workshop. Detailed descriptions are much appreciated: brief description of all models and experiments tested, ablations, visualizations, things that did not work, datasets, pre-trained models, etc. You can share qualitative results via shared folder at google drive, dropbox, etc.
\end{enumerate}

\textbf{If you participate in both Track 1 and 2, you only need to submit 1 factsheet}.
This factsheet, and the source codes/models/executables (as specified \href{https://github.com/eduardzamfir/NTIRE23-RTSR#evaluation-of-your-submission}{here}) must be sent to \textbf{all of the NTIRE 2023 Real-Time Super-Resolution Challenge organizers} by email. We accept download links from your website, google drive, dropbox, etc. When using cloud services, please remember to allow sharing and consider the traffic limit of your service provider. If there is any problem, we will contact the team leader.

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|}
    \hline
    Organizer name & Email \\
    \hline
    Marcos Conde  & marcos.conde@uni-wuerzburg.de  \\
    Eduard Zamfir & eduard-sebastian.zamfir@uni-wuerzburg.de  \\
    Radu Timofte  & radu.timofte@uni-wuerzburg.de \\
    \hline
\end{tabular}
\vspace{-0.5cm}
\end{center}
\end{table}
 \newpage
\section*{Email final submission guide}

\texttt{
To: marcos.conde@uni-wuerzburg.de, \\
eduard-sebastian.zamfir@uni-wuerzburg.de, \\
radu.timofte@uni-wuerzburg.de\\
cc: your\_team\_members\\
Title: NTIRE 2023 Real-Time Super-Resolution Challenge - TEAM\_NAME\\
}

Body contents should include:

a) the challenge name (AND TRACKS): NTIRE 2023 Real-Time Super-Resolution Challenge

b) team name

c) team leader's name and email address

d) rest of the team members

e) team name and user names on CodaLab competitions

f) executable/models/source code attached or download links. We will run and benchmark the models following \url{https://github.com/eduardzamfir/NTIRE23-RTSR#evaluation-of-your-submission}.

g) factsheet attached. You can also provide a link to \textbf{overleaf}. Only we, the organizers, will be able to read it. Factsheet must be a compiled pdf file together with a zip with .tex factsheet source files (including figures with good resolution).

\section{Team details}

\begin{itemize}
\item Team name                                  
\item Team leader name                           
\item Team leader institution and email (Please make sure is an active email)
\item Rest of the team members        
\item Team website URL (if any)                   
\item Affiliations
\item Usernames on the NTIRE 2023 Real-Time Super-Resolution Codalab leaderboard (development/validation and testing phases)
\item Link to the codes/executables of the solution(s) following \url{https://github.com/eduardzamfir/NTIRE23-RTSR}
\end{itemize}

\section{Contribution details}

\begin{itemize}
\item Title of the contribution
\item General method description (Summary)
\item References                                               
\item have you tested previously published methods? (yes/no) If yes, please specify which methods and the results/problems you found.
\item Other methods and baselines tested (even if results were not top competitive).
\end{itemize}

\section{Global Method Description}
Please describe your method.

\begin{itemize}
\item Which pre-trained or external methods / models have been used (for any stage, if any) 
\item Which datasets did you use for training? How did you pre-process the dataset?
\item Training and Inference description
\item Model optimization: how did you design your efficient model? do you use pruning? re-parametrization?
\item Quantitative and qualitative advantages of the solution (optional)
\item Results of the comparison to other approaches (if any)
\item Results on other benchmarks (if any)
\item Novelty degree of the solution and if it has been previously published
\end{itemize}

PLEASE ADD A DIAGRAM.
\begin{figure}
    \centering
    %\includegraphics{}
    \framebox{}
    \caption{YOUR DIAGRAM HERE}
    \label{fig:my_diagram}
\end{figure}

It is OK if the proposed solution is based on other works (papers, reports, Internet sources (links), etc), please \textbf{cite} them.

\vspace{4mm}
Please fill the following table specifying the technical information (besides writing it), should take 1 minute. 
%FILL THIS TABLE PLEASE
% Input:         size of the input patch used for TRAINING
% Training time: in hours, how many hours do you train?
% Attention:     Do you use attention mechanisms? If YES, indicate how in the technical details below
% Optimization:  Do you use quantization or prunning?
% Params:        Number of parameters of the model
% GPU:           GPU used in yout experiments

\begin{table}[]
    \centering
    \resizebox{\textwidth}{!}{
    \begin{tabular}{c|c|c|c|c|c|c}
        Input & Training Time & Attention & Quantization & \# Params. (M) & GPU  \\
        \hline
         (256,256,3) & 12h & Yes/No & Yes/No & 5 Million & A100
    \end{tabular}
    }
    \caption{FILL THIS TABLE PLEASE}
    \label{tab:my_label}
\end{table}

\section{Technical details}
Please make sure to write about the language and implementation details: framework, optimizer, learning rate, GPU, datasets used for training, training time, training strategies, efficiency optimization strategies.

\vspace{4mm}
\noindent Any particularities of the solution for this competition in comparison to other SR challenges (if applicable).

\section{Other details}
\begin{itemize}

\item Planned submission of a solution(s) description paper at NTIRE 2023 workshop [YES/ NO].

\item General comments and impressions of the NTIRE 2023 Real-Time Super-Resolution Challenge (we appreciate your feedback to improve in future editions).

\item What do you expect from a new challenge in image restoration, enhancement and manipulation?

\end{itemize}

\end{document}

### 2023-03-18 NTIRE 2023 Efficient SR Challenge Factsheet/EfficientSR_factsheet.tex
基本信息

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{NTIRE 2023 Efficient SR Challenge Factsheet\\-title of the contribution-}
+\title{NTIRE 2023 Efficient SR Challenge Factsheet\\PRFDN: High Parallelism Distillation Network For Image Super-resolution}
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Daheng Yin, Baijun Chen, Mengyang Liu\\
+School of Computer Science and Engineering, Southeast University\\
+Nanjing, Jiangsu\\
+{\tt\small {yindaheng98, bjchen, myliu}@seu.edu.cn}
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
 }
@@
 \begin{itemize}
-\item Team name                                  
-\item Team leader name                           
-\item Team leader address, phone number, and email 
-\item Rest of the team members        
-\item Team website URL (if any)                   
-\item Affiliation
-\item Affiliation of the team and/or team members with NTIRE 2023 sponsors (check the workshop website)
-\item User names and entries on the NTIRE 2023 Codalab competitions (development/validation and testing phases)
-\item Best scoring entries of the team during development/validation phase
-\item Link to the codes/executables of the solution(s)
+\item Team name: SEU\_CNII
+\item Team leader name: Daheng Yin
+\item Team leader address, phone number, and email: \\School of Computer Science and Engineering, Southeast University; \\+86 188 5189 9135; yindaheng98@seu.edu.cn
+\item Rest of the team members: Baijun Chen, Mengyang Liu
+\item Team website URL (if any): N/A
+\item Affiliation: School of Computer Science and Engineering, Southeast University
+\item User names and entries on the NTIRE 2023 Codalab competitions (development/validation and testing phases): yindaheng98
+\item Best scoring entries of the team during development/validation phase:\\PSNR 28.993
+\item Link to the codes/executables of the solution(s): \url{https://github.com/yindaheng98/NTIRE23-RTSR}
 \end{itemize}

### 2023-03-18 NTIRE 2023 RTSR Factsheet/main.tex
基本信息

@@
 %%% Add Your names and affiliations.
-\author{\textcolor{red}{Your Teamname Here}\\
-\textcolor{red}{Your names}\thanks{\textcolor{blue}{Affiliations}}\\
+\author{\textcolor{red}{SEU\_CNII}\\
+\textcolor{red}{Daheng Yin, Baijun Chen, Mengyang Liu}\thanks{\textcolor{blue}{School of Computer Science and Engineering, Southeast University}}\\
 }
@@
 \begin{itemize}
-\item Team name                                  
-\item Team leader name                           
-\item Team leader institution and email (Please make sure is an active email)
-\item Rest of the team members        
-\item Team website URL (if any)                   
-\item Affiliations
-\item Usernames on the NTIRE 2023 Real-Time Super-Resolution Codalab leaderboard (development/validation and testing phases)
-\item Link to the codes/executables of the solution(s) following \url{https://github.com/eduardzamfir/NTIRE23-RTSR}
+\item Team name: SEU\_CNII
+\item Team leader name: Daheng Yin
+\item Team leader institution and email: School of Computer Science and Engineering, Southeast University; yindaheng98@seu.edu.cn
+\item Rest of the team members: Baijun Chen, Mengyang Liu
+\item Team website URL (if any): N/A
+\item Affiliations: School of Computer Science and Engineering, Southeast University
+\item Usernames on the NTIRE 2023 Real-Time Super-Resolution Codalab leaderboard (development/validation and testing phases): yindaheng98
+\item Link to the codes/executables of the solution(s) following \url{https://github.com/yindaheng98/NTIRE23-RTSR}
 \end{itemize}
@@
 \begin{itemize}
-\item Title of the contribution
+\item Title of the contribution\\PRFDN: High Parallelism Distillation Network For Image Super-resolution
 \item General method description (Summary)

### 2023-03-19 NTIRE 2023 RTSR Factsheet/main.tex
保存

@@
 \usepackage{colortbl, color, xcolor}
+\usepackage{subcaption}
 
@@
 \item Title of the contribution\\PRFDN: High Parallelism Distillation Network For Image Super-resolution
-\item General method description (Summary)
+\item General method description (Summary)\\Our methods
 \item References                                               
 \item have you tested previously published methods? (yes/no) If yes, please specify which methods and the results/problems you found.
-\item Other methods and baselines tested (even if results were not top competitive).
+\item Other methods and baselines tested (even if results were not top competitive).\\We have tested % TODO: 通道扩增
 \end{itemize}
@@
 \section{Global Method Description}
-Please describe your method.
+% TODO: 参照去年的文章来，一页纸就够
+We proposed Parallel RFDN (PRFDN) as is shown in Fig.\ref{fig:PRFDN}.
+Our method consists of three stages to transform a pre-trained RFDN into PRFDN.
+\begin{enumerate}
+    \item Branching.
+To accelerate the inference, we first consider reducing the data dependency in the model to achieve higher parallelism.
+Our method disentangles the sequentially computed trunks into branches.
+As is shown in figure \ref{fig:Branching}, after the branching, the major part of the model will consist of four independent branches that can calculate in parallel.
+To improve the accuracy, we also design a small SR block (SRFDB) based on the RFDB of RFDN and add them before the input of each branch.
+    \item Training.
+Since we only change the data flow but not the structure of RFDB, the pre-trained RFDN parameters can still be loaded into the major part of our branch model (only except for those SRFDBs).
+To benefit from the pre-training, we load the pre-trained RFDN parameters into our branch model before training our branch model.
+    \item Re-parametrization.
+Without much data dependency, branches in our model can be computed in parallel.
+However, a single GPU cannot compute two or more different models in parallel.
+To address this issue and achieve parallel computing of multiple branches on a single GPU, we should merge the four branches into a single branch.
+As is shown in figure \ref{fig:Branching}, we realize that the major part of these four branches (RFDBs and SRFDBs) have exactly the same structure but different parameters, so we merge and re-parametrized the RFDBs and SRFDBs into a single branch.
+More specifically, we create a bigger RFDB and a bigger SRFDB with bigger convolution layers and move the weight and bias from the RFDBs and SRFDBs into them.
+After re-parametrization, we get a bigger model that is equivalent to that of the branches of the branch model computed in parallel on a single GPU.
+    \item Pruning.
+The re-parametrized model is big.
+To further accelerate the inference, we applied channel pruning on our re-parametrized model, as is shown in figure \ref{fig:Pruning}.
+To accurately extract the channel dependency for pruning, we first replace each concatenate and split operation with an equivalent convolution operation.
+After replacement, we used torch-pruning to prune the model and finetune the model between each pruning step.
+%TODO: 需要cite
+\end{enumerate}
 
 \begin{itemize}
-\item Which pre-trained or external methods / models have been used (for any stage, if any) 
-\item Which datasets did you use for training? How did you pre-process the dataset?
-\item Training and Inference description
+\item Which pre-trained or external methods / models have been used (for any stage, if any) \\ Our method is based on the pre-trained RFDN baseline.
+\item Which datasets did you use for training?
+How did you pre-process the dataset?
+\\ We combined the training set of LSDIR, DIV2K, Flickr2K and OST as our training set, and take the validating set of DIV2K for validation.
+\item Training and Inference description \\ 
 \item Model optimization: how did you design your efficient model? do you use pruning? re-parametrization?
-\item Quantitative and qualitative advantages of the solution (optional)
-\item Results of the comparison to other approaches (if any)
-\item Results on other benchmarks (if any)
+\item Quantitative and qualitative advantages of the solution (optional): N/A
+\item Results of the comparison to other approaches (if any): N/A
+\item Results on other benchmarks (if any): N/A
 \item Novelty degree of the solution and if it has been previously published
@@
     \centering
-    %\includegraphics{}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
         \framebox{}
+        \caption{RFDN}
+        \label{fig:RFDN}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \framebox{}
+        \caption{Branching}
+        \label{fig:Branching}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \framebox{}
+        \caption{Re-parametrization}
+        \label{fig:Re-parametrization}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \framebox{}
+        \caption{Pruning}
+        \label{fig:Pruning}
+    \end{subfigure}
     \caption{YOUR DIAGRAM HERE}
-    \label{fig:my_diagram}
+    \label{fig:PRFDN}
 \end{figure}

### 2023-03-19 NTIRE 2023 RTSR Factsheet/main.tex
就差图了

@@
 \item Title of the contribution\\PRFDN: High Parallelism Distillation Network For Image Super-resolution
-\item General method description (Summary)\\Our methods
-\item References                                               
-\item have you tested previously published methods? (yes/no) If yes, please specify which methods and the results/problems you found.
-\item Other methods and baselines tested (even if results were not top competitive).\\We have tested % TODO: 通道扩增
+\item General method description (Summary)\\We proposed Parallel RFDN (PRFDN) based on the pre-trained RFDN\cite{liu2020residual} as is shown in figure \ref{fig:PRFDN}.
+Our method disentangles the sequentially computed trunks in RFDN into branches (figure \ref{fig:Branching}) and performs re-parametrization to make these branches inference in parallel on single devices.
+After that, we further perform pruning on the model (figure \ref{fig:Pruning}) and finetune it to achieve higher performance.
+\item References: RFDN\cite{liu2020residual}, Torch-Pruning\cite{fang2023depgraph}
+\item have you tested previously published methods? (yes/no) If yes, please specify which methods and the results/problems you found. N/A
+\item Other methods and baselines tested (even if results were not top competitive). N/A
 \end{itemize}
@@
 \section{Global Method Description}
-% TODO: 参照去年的文章来，一页纸就够
-We proposed Parallel RFDN (PRFDN) as is shown in Fig.\ref{fig:PRFDN}.
-Our method consists of three stages to transform a pre-trained RFDN into PRFDN.
+
+We proposed Parallel RFDN (PRFDN) as is shown in figure \ref{fig:PRFDN}.
+Our method consists of four stages to transform a pre-trained RFDN into PRFDN.
 \begin{enumerate}
@@
 To address this issue and achieve parallel computing of multiple branches on a single GPU, we should merge the four branches into a single branch.
-As is shown in figure \ref{fig:Branching}, we realize that the major part of these four branches (RFDBs and SRFDBs) have exactly the same structure but different parameters, so we merge and re-parametrized the RFDBs and SRFDBs into a single branch.
+As is shown in figure \ref{fig:Re-parametrization}, we realize that the major part of these four branches (RFDBs and SRFDBs) have exactly the same structure but different parameters, so we merge and re-parametrized the RFDBs and SRFDBs into a single branch.
 More specifically, we create a bigger RFDB and a bigger SRFDB with bigger convolution layers and move the weight and bias from the RFDBs and SRFDBs into them.
@@
 To accurately extract the channel dependency for pruning, we first replace each concatenate and split operation with an equivalent convolution operation.
-After replacement, we used torch-pruning to prune the model and finetune the model between each pruning step.
-%TODO: 需要cite
+After replacement, we used Torch-Pruning\cite{fang2023depgraph} to prune the model and finetune the model between each pruning step.
 \end{enumerate}
 
-\begin{itemize}
-\item Which pre-trained or external methods / models have been used (for any stage, if any) \\ Our method is based on the pre-trained RFDN baseline.
-\item Which datasets did you use for training?
-How did you pre-process the dataset?
-\\ We combined the training set of LSDIR, DIV2K, Flickr2K and OST as our training set, and take the validating set of DIV2K for validation.
-\item Training and Inference description \\ 
-\item Model optimization: how did you design your efficient model? do you use pruning? re-parametrization?
-\item Quantitative and qualitative advantages of the solution (optional): N/A
-\item Results of the comparison to other approaches (if any): N/A
-\item Results on other benchmarks (if any): N/A
-\item Novelty degree of the solution and if it has been previously published
-\end{itemize}
-
-PLEASE ADD A DIAGRAM.
 \begin{figure}
@@
     \end{subfigure}
-    \caption{YOUR DIAGRAM HERE}
+    \caption{Transform a pre-trained RFDN into PRFDN}
     \label{fig:PRFDN}
 \end{figure}
-
-It is OK if the proposed solution is based on other works (papers, reports, Internet sources (links), etc), please \textbf{cite} them.
 
@@
         \hline
-         (256,256,3) & 12h & Yes/No & Yes/No & 5 Million & A100
+         (256,256,3) & 12h & No & Yes & 5 Million & RTX 3070 8G
     \end{tabular}
@@
 \section{Technical details}
-Please make sure to write about the language and implementation details: framework, optimizer, learning rate, GPU, datasets used for training, training time, training strategies, efficiency optimization strategies.
+\begin{itemize}
+    \item Language: Python
+    \item Framework: Pytorch, Torch-Pruning\cite{fang2023depgraph}
+    \item Optimizer: AdaM
+    \item Learning rate: 1e-5 before re-parametrization, 1e-6 after re-parametrization
+    \item GPU: RTX 3070 8G
+    \item Datasets for training: LSDIR and DIV2K
+\end{itemize}
 
@@
 \noindent Any particularities of the solution for this competition in comparison to other SR challenges (if applicable).
+N/A
 
@@
 \item Planned submission of a solution(s) description paper at NTIRE 2023 workshop [YES/ NO].
+YES
 
@@
 
+Positive impression: Scripts for running the models and measuring metrics are well organized.
+
+Negative impression: Instructions are not clear (e.g. there are some posts in the forum saying that they cannot find the test set, but none of the organizers respond).
+
+A small suggestion: Create a group in instant messaging apps (e.g. Discord or Telegram) for convenient communication.
+
 \item What do you expect from a new challenge in image restoration, enhancement and manipulation?
+Real-time video super-resolution; Efficient compressed video restoration.
 
@@
 
+%%%%%%%%% REFERENCES
+{\small
+\bibliographystyle{ieee_fullname}
+\bibliography{egbib}
+}
 \end{document}

### 2023-03-19 NTIRE 2023 Efficient SR Challenge Factsheet/EfficientSR_factsheet.tex
ok

@@
 
-You should describe your proposed solution in detail. This part is equivalent to the methodology part of a conference paper submission. The description should cover the following details.
+We proposed Parallel RFDN (PRFDN) as is shown in figure \ref{fig:PRFDN}.
+Our method consists of four stages to transform a pre-trained RFDN\cite{liu2020residual} into PRFDN.
+\begin{enumerate}
+    \item Branching.
+To accelerate the inference, we first consider reducing the data dependency in the model to achieve higher parallelism.
+Our method disentangles the sequentially computed trunks into branches.
+As is shown in figure \ref{fig:Branching}, after the branching, the major part of the model will consist of four independent branches that can calculate in parallel.
+To improve the accuracy, we also design a small SR block (SRFDB) based on the RFDB of RFDN and add them before the input of each branch.
+    \item Training.
+Since we only change the data flow but not the structure of RFDB, the pre-trained RFDN parameters can still be loaded into the major part of our branch model (only except for those SRFDBs).
+To benefit from the pre-training, we load the pre-trained RFDN parameters into our branch model before training our branch model.
+    \item Re-parametrization.
+Without much data dependency, branches in our model can be computed in parallel.
+However, a single GPU cannot compute two or more different models in parallel.
+To address this issue and achieve parallel computing of multiple branches on a single GPU, we should merge the four branches into a single branch.
+As is shown in figure \ref{fig:Re-parametrization}, we realize that the major part of these four branches (RFDBs and SRFDBs) have exactly the same structure but different parameters, so we merge and re-parametrized the RFDBs and SRFDBs into a single branch.
+More specifically, we create a bigger RFDB and a bigger SRFDB with bigger convolution layers and move the weight and bias from the RFDBs and SRFDBs into them.
+After re-parametrization, we get a bigger model that is equivalent to that of the branches of the branch model computed in parallel on a single GPU.
+    \item Pruning.
+The re-parametrized model is big.
+To further accelerate the inference, we applied channel pruning on our re-parametrized model, as is shown in figure \ref{fig:Pruning}.
+To accurately extract the channel dependency for pruning, we first replace each concatenate and split operation with an equivalent convolution operation.
+After replacement, we used Torch-Pruning\cite{fang2023depgraph} to prune the model and finetune the model between each pruning step.
+\end{enumerate}
 
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{\linewidth}
+		\centering
+        \framebox{}
+        \caption{RFDN}
+        \label{fig:RFDN}
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+		\centering
+        \framebox{}
+        \caption{Branching}
+        \label{fig:Branching}
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+		\centering
+        \framebox{}
+        \caption{Re-parametrization}
+        \label{fig:Re-parametrization}
+    \end{subfigure}
+    \begin{subfigure}[b]{\linewidth}
+		\centering
+        \framebox{}
+        \caption{Pruning}
+        \label{fig:Pruning}
+    \end{subfigure}
+    \caption{Transform a pre-trained RFDN into PRFDN}
+    \label{fig:PRFDN}
+\end{figure}
+
+\section{Technical details}
 \begin{itemize}
-\item General method description (How is the network designed.)                                
-%\item Description of the particularities of the solutions deployed for each of the challenge competitions or tracks
-\item Representative image / diagram / pipeline of the method(s)  
-\item Training strategy
-\item Experimental results
-\item References                                               
+    \item Language: Python
+    \item Framework: Pytorch, Torch-Pruning\cite{fang2023depgraph}
+    \item Optimizer: AdaM
+    \item Learning rate\\Before re-parametrization: 1e-5 in general, if the loss cannot decrease after a lot of epochs, then descrease to 5e-6\\After re-parametrization: 1e-6
+    \item GPU: RTX 3070 8G
+    \item Datasets for training: LSDIR and DIV2K
 \end{itemize}
-
-Additionally, you can refer to the following items to detail your description.
-\begin{itemize}
-\item Total method complexity (number of parameters, FLOPs, GPU memory consumption, number of activations, runtime)
-\item Which pre-trained or external methods / models have been used (for any stage, if any) 
-\item Which additional data has been used in addition to the provided NTIRE training and validation data (at any stage, if any) 
-\item Training description
-\item Testing description
-\item Quantitative and qualitative advantages of the proposed solution
-\item Results of the comparison to other approaches (if any)
-\item Results on other benchmarks (if any)
-\item Novelty degree of the solution and if it has been previously published
-\item It is OK if the proposed solution is based on other works (papers, reports, Internet sources (links), etc).
-It is ethically wrong and a misconduct if you are not properly giving credits and hide this information.
-\end{itemize}
-
-% \section{Technical details}
-% \begin{itemize}
-% \item Language and implementation details (including platform, memory, parallelization requirements)
-% \item Human effort required for implementation, training and validation?
-% \item Training/testing time? Runtime at test per image (\textbf{including ensemble}).
-% \item Comment the robustness and generality of the proposed solution(s)? 
-% % Is it easy to deploy it for other sets of downscaling operators? 
-% \item Comment the efficiency of the proposed solution(s)?
-% \end{itemize}
 
@@
 \begin{itemize}
-\item Planned submission of a solution(s) description paper at NTIRE 2023 workshop.
+\item Planned submission of a solution(s) description paper at NTIRE 2023 workshop. YES
 \item General comments and impressions of the NTIRE 2023 challenge.
+
+Positive impression: Scripts for running the models and measuring metrics are well organized.
+
+Negative impression: Instructions are not clear (e.g. there are some posts in the forum saying that they cannot find the test set, but none of the organizers respond).
+
+A small suggestion: Create a group in instant messaging apps (e.g. Discord or Telegram) for convenient communication.
+
 \item What do you expect from a new challenge in image restoration, enhancement and manipulation?
-\item Other comments: encountered difficulties, fairness of the challenge, proposed subcategories, proposed evaluation method(s), etc.
+Real-time video super-resolution; Efficient compressed video restoration.
+\item Other comments: encountered difficulties, fairness of the challenge, proposed subcategories, proposed evaluation method(s), etc. N/A
 \end{itemize}

### 2023-03-19 svg_to_pdf.sh
图都ok

@@ -1,0 +1,4 @@
+inkscape --export-filename=RFDN.pdf RFDN.svg
+inkscape --export-filename=Branching.pdf Branching.svg
+inkscape --export-filename=Re-parametrization.pdf Re-parametrization.svg
+inkscape --export-filename=Pruning.pdf Pruning.svg

### 2023-03-19 NTIRE 2023 Efficient SR Challenge Factsheet/EfficientSR_factsheet.tex
写好了
Init method details

@@
 
-We proposed Parallel RFDN (PRFDN) as is shown in figure \ref{fig:PRFDN}.
-Our method consists of four stages to transform a pre-trained RFDN\cite{liu2020residual} into PRFDN.
-\begin{enumerate}
-    \item Branching.
-To accelerate the inference, we first consider reducing the data dependency in the model to achieve higher parallelism.
-Our method disentangles the sequentially computed trunks into branches.
-As is shown in figure \ref{fig:Branching}, after the branching, the major part of the model will consist of four independent branches that can calculate in parallel.
-To improve the accuracy, we also design a small SR block (SRFDB) based on the RFDB of RFDN and add them before the input of each branch.
-    \item Training.
-Since we only change the data flow but not the structure of RFDB, the pre-trained RFDN parameters can still be loaded into the major part of our branch model (only except for those SRFDBs).
-To benefit from the pre-training, we load the pre-trained RFDN parameters into our branch model before training our branch model.
-    \item Re-parametrization.
-Without much data dependency, branches in our model can be computed in parallel.
-However, a single GPU cannot compute two or more different models in parallel.
-To address this issue and achieve parallel computing of multiple branches on a single GPU, we should merge the four branches into a single branch.
-As is shown in figure \ref{fig:Re-parametrization}, we realize that the major part of these four branches (RFDBs and SRFDBs) have exactly the same structure but different parameters, so we merge and re-parametrized the RFDBs and SRFDBs into a single branch.
-More specifically, we create a bigger RFDB and a bigger SRFDB with bigger convolution layers and move the weight and bias from the RFDBs and SRFDBs into them.
-After re-parametrization, we get a bigger model that is equivalent to that of the branches of the branch model computed in parallel on a single GPU.
-    \item Pruning.
-The re-parametrized model is big.
-To further accelerate the inference, we applied channel pruning on our re-parametrized model, as is shown in figure \ref{fig:Pruning}.
-To accurately extract the channel dependency for pruning, we first replace each concatenate and split operation with an equivalent convolution operation.
-After replacement, we used Torch-Pruning\cite{fang2023depgraph} to prune the model and finetune the model between each pruning step.
-\end{enumerate}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{\linewidth}
-		\centering
-        \framebox{}
-        \caption{RFDN}
-        \label{fig:RFDN}
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-		\centering
-        \framebox{}
-        \caption{Branching}
-        \label{fig:Branching}
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-		\centering
-        \framebox{}
-        \caption{Re-parametrization}
-        \label{fig:Re-parametrization}
-    \end{subfigure}
-    \begin{subfigure}[b]{\linewidth}
-		\centering
-        \framebox{}
-        \caption{Pruning}
-        \label{fig:Pruning}
-    \end{subfigure}
-    \caption{Transform a pre-trained RFDN into PRFDN}
-    \label{fig:PRFDN}
-\end{figure}
+We improve RFDN\cite{liu2020residual} model based on the "Train Big, Then Compress" theory proposed by \cite{li2020trainlarge}.
+We first expand all channels of operation in RFDN exclude pixelshuffle operation with 2x factor and then train it which is a big model training and achieved better results for its larger model capacity.
+After training, a heavy compression followed.
+We utilize a dynamic structure pruning method\cite{fang2023depgraph} to compress model and finetune it iteratively.
+% TODO: add detailed configuration and hyperparameters.
 

### 2023-03-20 NTIRE 2023 RTSR Factsheet/main.tex
ok
写好了
save

@@
 We proposed Parallel RFDN (PRFDN) as is shown in figure \ref{fig:PRFDN}.
-Our method consists of four stages to transform a pre-trained RFDN into PRFDN.
+Our method consists of four stages to transform a pre-trained RFDN\cite{liu2020residual} into PRFDN.
 \begin{enumerate}
@@
 		\centering
-        \framebox{}
+        \includegraphics[width=\textwidth]{../RFDN.pdf}
         \caption{RFDN}
@@
 		\centering
-        \framebox{}
+        \includegraphics[width=\textwidth]{../Branching.pdf}
         \caption{Branching}
@@
 		\centering
-        \framebox{}
+        \includegraphics[width=\textwidth]{../Re-parametrization.pdf}
         \caption{Re-parametrization}
@@
 		\centering
-        \framebox{}
+        \includegraphics[width=\textwidth]{../Pruning.pdf}
         \caption{Pruning}
@@
     \resizebox{\textwidth}{!}{
-    \begin{tabular}{c|c|c|c|c|c|c}
-        Input & Training Time & Attention & Quantization & \# Params. (M) & GPU  \\
+    \begin{tabular}{c|c|c|c|c|c|c|c}
+        Track & Input & Training Time & Attention & Quantization & \# Params. (M) & GPU  \\
         \hline
-         (256,256,3) & 12h & No & Yes & 5 Million & RTX 3070 8G
+        1 & (678,1020,3) & 16h & No & No & 0.0299 Million & RTX 3070 8G \\
+        2 & (512,680,3) & 16h & No & No & 0.0629 Million & RTX 3070 8G \\
     \end{tabular}

### 2023-03-22 NTIRE 2023 RTSR Factsheet/main.tex
final
最终保存

@@
     \begin{tabular}{c|c|c|c|c|c|c|c}
-        Track & Input & Training Time & Attention & Quantization & \# Params. (M) & GPU  \\
+        Track & Input & Data range & Training Time & Attention & Quantization & \# Params. (M) & GPU  \\
         \hline
-        1 & (678,1020,3) & 16h & No & No & 0.0299 Million & RTX 3070 8G \\
-        2 & (512,680,3) & 16h & No & No & 0.0629 Million & RTX 3070 8G \\
+        1 & (678,1020,3) & 255 & 16h & No & No & 0.0299 Million & RTX 3070 8G \\
+        2 & (512,680,3) & 255 & 16h & No & No & 0.0629 Million & RTX 3070 8G \\
     \end{tabular}
@@
 
-Negative impression: Instructions are not clear (e.g. there are some posts in the forum saying that they cannot find the test set, but none of the organizers respond).
+Negative impression: There are some posts in the forum saying that they cannot find the test set, but none of the organizers respond.
 

### 2023-04-03 NTIRE 2023 RTSR Paper/PaperForReview.tex
save

% CVPR 2023 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[review]{cvpr}      % To produce the REVIEW version
%\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Author Guidelines for \confName~Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
   The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Single image super-resolution (SISR) is a computer vision technique to reconstruct high-resolution images from low-resolution images. Deep convolution neural networks have shown impressive performance in this area and many deep learning-based methods have been proposed to address this ill-posed problem.
This technique has been used in many applications (e.g. video gaming and video streaming) to achieve displays with high resolution and high refresh rates and some of the related applications have been deployed on lots of mobile devices.
However, mobile phones have a power-constrained design with a dedicated power supply, which makes efficient image super-resolution (EISR) a growing interest.

Efficient network design is key to achieving better performance in EISR.
To make the network more efficient for resource-limited devices, researchers are designing generic lightweight networks with reduced parameters through methods like network pruning and knowledge distillation.
However, when the model size becomes sufficiently small, these methods fail to further increase the frame rate of super-resolution. This is because reducing the computational scale of each layer of the model beyond the point where the GPU is fully loaded does not improve the inference speed of the model, if the length of serial executed layers cannot be reduced.
Therefore, some EISR design involves careful consideration of network architecture, design, and utilization of limited features to generate more representative features for super-resolution, which can use fewer layers to achieve a good super-resolution quality.

Moreover, recent years have witnessed the wide use of U-Net in the design of deep neural networks. 
Many designs of the EISR model also adopted the U-Net architecture, and the RFDN\cite{liu2020residual} is a representative example, which won the first prize in the AIM 2020 competition. 
Through the observation of the U-Net structure, we found that the model's main structure can be transformed into mutually independent branches by deconstructing its branching structure, thereby increasing parallelism. 
Furthermore, multiple branches can be executed in parallel on the same GPU by reparameterization. 
Within the GPU's capacity, this method can reduce the number of layers that are executed serially in the network, therefore improving the inference speed.

In this paper, we proposed Parallel RFDN (PRFDN) based on the pre-trained RFDN. Our method disentangles the sequentially computed trunks in RFDN into branches and performs re-parametrization to make these branches inference in parallel on single devices. After that, we further perform pruning on the model and finetune it to achieve higher performance.

Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.

\subsection{Paper ID}
Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.

\subsection{Methods}

Please number all of your sections and displayed equations as in these examples:
\begin{equation}
  E = m\cdot c^2
  \label{eq:important}
\end{equation}
and
\begin{equation}
  v = a\cdot t.
  \label{eq:also-important}
\end{equation}
It is important for readers to be able to refer to any particular equation.
Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
All authors will benefit from reading Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind review.
Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
That is all.
(But see below for tech reports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
it says that you are building on her work.
If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:
\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
Then submit the tech report as supplemental material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
solution.
The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.
Do not write ``We show how to improve our previous work [Anonymous, 1968].
This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors.
Instead write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.
   This system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
   Ours handles it by including a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
   It displayed the following behaviours, which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
For your results, however, you should not identify yourself and should not mention your participation in the challenge.
Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}

   \caption{Example of caption.
   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
   \label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a sentence-ending space.
So \eg is correct, {\em e.g.} is not.
The provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
However, use it only when there are three or more authors.
Thus, the following is correct:
   ``Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.

% Update the cvpr.cls to do the following automatically.
% For this citation style, keep multiple citations in numerical (not
% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
% \cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
  \centering
  \begin{subfigure}{0.68\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{An example of a subfigure.}
    \label{fig:short-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{Another example of a subfigure.}
    \label{fig:short-b}
  \end{subfigure}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}
\label{sec:formatting}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
The second and following pages should begin 1 inch (2.54 cm) from the top edge.
On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
high.
%
Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
The \LaTeX\ template takes care of this when used properly.

%-------------------------------------------------------------------------
\subsection{Type style and fonts}

Wherever Times is specified, Times Roman may also be used.
If neither is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE.
Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type.
This information is to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT.
Type main text in 10-point Times, single-spaced.
Do NOT use double-spacing.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Make sure your text is fully justified---that is, flush left and flush right.
Please do not place any additional blank lines between paragraphs.

Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-, second-, and third-order headings.

FIRST-ORDER HEADINGS.
(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS.
(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{Cross-references}

For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.

\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.
Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.

If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2023-04-03 NTIRE 2023 RTSR Paper/PaperForReview.tex
大大大

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{\LaTeX\ Author Guidelines for \confName~Proceedings}
+\title{Branchy parallelized U-net structure
+
+Branching, finetune, reparameterized, pruning
+
+paralleled 
+branched
+
+Pruning reparameterized super-resolution model}
+%多路径
 
@@
 \subsection{Methods}
+
+We proposed Parallel RFDN (PRFDN) as is shown in figure \ref{fig:PRFDN}.
+Our method consists of four stages to transform a pre-trained RFDN\cite{liu2020residual} into PRFDN.
+\begin{enumerate}
+    \item Branching.
+To accelerate the inference, we first consider reducing the data dependency in the model to achieve higher parallelism.
+Our method disentangles the sequentially computed trunks into branches.
+As is shown in figure \ref{fig:Branching}, after the branching, the major part of the model will consist of four independent branches that can calculate in parallel.
+To improve the accuracy, we also design a small SR block (SRFDB) based on the RFDB of RFDN and add them before the input of each branch.
+    \item Training.
+Since we only change the data flow but not the structure of RFDB, the pre-trained RFDN parameters can still be loaded into the major part of our branch model (only except for those SRFDBs).
+To benefit from the pre-training, we load the pre-trained RFDN parameters into our branch model before training our branch model.
+    \item Re-parametrization.
+Without much data dependency, branches in our model can be computed in parallel.
+However, a single GPU cannot compute two or more different models in parallel.
+To address this issue and achieve parallel computing of multiple branches on a single GPU, we should merge the four branches into a single branch.
+As is shown in figure \ref{fig:Re-parametrization}, we realize that the major part of these four branches (RFDBs and SRFDBs) have exactly the same structure but different parameters, so we merge and re-parametrized the RFDBs and SRFDBs into a single branch.
+More specifically, we create a bigger RFDB and a bigger SRFDB with bigger convolution layers and move the weight and bias from the RFDBs and SRFDBs into them.
+After re-parametrization, we get a bigger model that is equivalent to that of the branches of the branch model computed in parallel on a single GPU.
+    \item Pruning.
+The re-parametrized model is big.
+To further accelerate the inference, we applied channel pruning on our re-parametrized model, as is shown in figure \ref{fig:Pruning}.
+To accurately extract the channel dependency for pruning, we first replace each concatenate and split operation with an equivalent convolution operation.
+After replacement, we used Torch-Pruning\cite{fang2023depgraph} to prune the model and finetune the model between each pruning step.
+\end{enumerate}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \includegraphics[width=\textwidth]{../RFDN.pdf}
+        \caption{RFDN}
+        \label{fig:RFDN}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \includegraphics[width=\textwidth]{../Branching.pdf}
+        \caption{Branching}
+        \label{fig:Branching}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \includegraphics[width=\textwidth]{../Re-parametrization.pdf}
+        \caption{Re-parametrization}
+        \label{fig:Re-parametrization}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \includegraphics[width=\textwidth]{../Pruning.pdf}
+        \caption{Pruning}
+        \label{fig:Pruning}
+    \end{subfigure}
+    \caption{Transform a pre-trained RFDN into PRFDN}
+    \label{fig:PRFDN}
+\end{figure*}
 

### 2023-04-04 NTIRE 2023 RTSR Paper/PaperForReview.tex
加引文

@@
 This technique has been used in many applications (e.g.
-video gaming and video streaming) to achieve displays with high resolution and high refresh rates and some of the related applications have been deployed on lots of mobile devices.
+video gaming\cite{10.1145/2751496.2751502} and video streaming\cite{kimNeuralEnhancedLiveStreaming2020,yeoNeuralAdaptiveContentaware2018,maoNeuralAdaptiveVideo2017}) to achieve displays with high resolution and high refresh rates and some of the related applications have been deployed on lots of mobile devices\cite{yeoNEMOEnablingNeuralenhanced2020,mehtaEVRNetEfficientVideo2021}.
 However, mobile phones have a power-constrained design with a dedicated power supply, which makes efficient image super-resolution (EISR) a growing interest.
@@
 Efficient network design is key to achieving better performance in EISR.
-To make the network more efficient for resource-limited devices, researchers are designing generic lightweight networks with reduced parameters through methods like network pruning and knowledge distillation.
+To make the network more efficient for resource-limited devices, researchers are designing generic lightweight networks with reduced parameters through methods like network pruning\cite{liuSplitSREndtoEndApproach2021,leeMobiSREfficientOnDevice2019,fang2023depgraph}, parallelism\cite{sandlerMobileNetV2InvertedResiduals2019,howardMobileNetsEfficientConvolutional2017,liuSplitSREndtoEndApproach2021,kongClassSRGeneralFramework2021} and knowledge distillation\cite{liu2020residual,khaniRealTimeVideoInference2021,taoCompressionGenerativePretrained2022,zhangDataFreeKnowledgeDistillation2021}.
 However, when the model size becomes sufficiently small, these methods fail to further increase the frame rate of super-resolution.
-This is because reducing the computational scale of each layer of the model beyond the point where the GPU is fully loaded does not improve the inference speed of the model, if the length of serial executed layers cannot be reduced.
-Therefore, some EISR design involves careful consideration of network architecture, design, and utilization of limited features to generate more representative features for super-resolution, which can use fewer layers to achieve a good super-resolution quality.
+This is because reducing the computational scale of each layer of the model beyond the point where the GPU is fully loaded does not improve the inference speed of the model, if the length of serially executed layers cannot be reduced.
+Therefore, lots of EISR designs\cite{liNTIRE2022Challenge2022,duFastMemoryEfficientNetwork2022,mehtaEVRNetEfficientVideo2021} involve careful consideration of network architecture, design, and utilization of limited features to generate more representative features for super-resolution, which can use fewer layers to achieve a good super-resolution quality.
 
-Moreover, recent years have witnessed the wide use of U-Net in the design of deep neural networks. 
+Moreover, recent years have witnessed the wide use of U-Net\cite{ronnebergerUNetConvolutionalNetworks2015} in the design of deep neural networks. 
 Many designs of the EISR model also adopted the U-Net architecture, and the RFDN\cite{liu2020residual} is a representative example, which won the first prize in the AIM 2020 competition. 
@@
 
-Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
-This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.
-
 \subsection{Paper ID}
@@
 Our method consists of four stages to transform a pre-trained RFDN\cite{liu2020residual} into PRFDN.
-\begin{enumerate}
-    \item Branching.
+
+\subsection{Branching}
 To accelerate the inference, we first consider reducing the data dependency in the model to achieve higher parallelism.
@@
 To improve the accuracy, we also design a small SR block (SRFDB) based on the RFDB of RFDN and add them before the input of each branch.
-    \item Training.
+
+\subsection{Training}
 Since we only change the data flow but not the structure of RFDB, the pre-trained RFDN parameters can still be loaded into the major part of our branch model (only except for those SRFDBs).
 To benefit from the pre-training, we load the pre-trained RFDN parameters into our branch model before training our branch model.
-    \item Re-parametrization.
+
+\subsection{Re-parametrization}
 Without much data dependency, branches in our model can be computed in parallel.
@@
 After re-parametrization, we get a bigger model that is equivalent to that of the branches of the branch model computed in parallel on a single GPU.
-    \item Pruning.
+
+\subsection{Pruning}
 The re-parametrized model is big.
@@
 After replacement, we used Torch-Pruning\cite{fang2023depgraph} to prune the model and finetune the model between each pruning step.
-\end{enumerate}
 

### 2023-04-04 NTIRE 2023 RTSR Paper/PaperForReview.tex
save

@@
 \usepackage{booktabs}
+\usepackage{bm}
 
@@
 Many designs of the EISR model also adopted the U-Net architecture, and the RFDN\cite{liu2020residual} is a representative example, which won the first prize in the AIM 2020 competition. 
-Through the observation of the U-Net structure, we found that the model's main structure can be transformed into mutually independent branches by deconstructing its branching structure, thereby increasing parallelism.
+Through the observation of the U-Net structure, we found its main structure can be transformed into mutually independent branches by deconstructing its branching structure, thereby increasing parallelism.
 Furthermore, multiple branches can be executed in parallel on the same GPU by reparameterization. 
@@
 To accelerate the inference, we first consider reducing the data dependency in the model to achieve higher parallelism. 
-Our method disentangles the sequentially computed trunks into branches.
+According to our observation, the main structure of U-Net can be transformed into mutually independent branches to increase parallelism. 
+Our method disentangles the sequentially computed trunks of RFDN into branches. 
 As is shown in figure \ref{fig:Branching}, after the branching, the major part of the model will consist of four independent branches that can calculate in parallel. 
 To improve the accuracy, we also design a small SR block (SRFDB) based on the RFDB of RFDN and add them before the input of each branch. 
+% This type of block 用于拟合多层RFDB的输出结果，使得输入到被展开后的RFDB block的输入与其在原始模型中接收的输入相近，从而以一个较小的代价保证模型精度
+This type of block is utilized to fit the output of cascaded RFDBs, such that the input to the disentangled RFDB block closely resembles the input received in the original RFDN.
+This ensures model accuracy at a reduced cost.
 
@@
 To benefit from the pre-training, we load the pre-trained RFDN parameters into our branch model before training our branch model.
+In this step, we first trained only SRFDBs for 100 epochs (on LSDIR dataset and DIV2K dataset) with freeze parameters in RFDBs, and then trained the whole model for 100 epochs.
 
@@
 To address this issue and achieve parallel computing of multiple branches on a single GPU, we should merge the four branches into a single branch. 
-As is shown in figure \ref{fig:Re-parametrization}, we realize that the major part of these four branches (RFDBs and SRFDBs) have exactly the same structure but different parameters, so we merge and re-parametrized the RFDBs and SRFDBs into a single branch.
-More specifically, we create a bigger RFDB and a bigger SRFDB with bigger convolution layers and move the weight and bias from the RFDBs and SRFDBs into them.
-After re-parametrization, we get a bigger model that is equivalent to that of the branches of the branch model computed in parallel on a single GPU.
+As is shown in figure \ref{fig:Branching}, three of these four branches have exactly the same structure with only different parameters, and the only difference between the remaining branch and the other branches is the absence of an RFDBS.
+Therefore, we should 1) merge those four convolution layers at the beginning of the branches into one, 2) merge those three RFDBS into one, and 3) merge those four RFDBs into one.
+
+In our method, we create a bigger RFDB and a bigger SRFDB with bigger convolution layers and move the weight and bias from the RFDBs and SRFDBs into them.
+More specifically, we merge the convolution layers according to the following derivation.
+
+Assuming $Y=Conv(X, K)$ represents a convolution layer,
+where $K\in\mathbb{R}^{c_o\times c\times h_k\times w_k}$ is the convolution kernel; $X\in\mathbb{R}^{c\times h\times w}$ is the input of convolution layer and $Y\in\mathbb{R}^{c_o\times h'\times w'}$ is the output;
+$c$, $h$, $w$ are the channel, height, and width of the input respectively; 
+$c_o$, $h'$, $w'$ are the channel, height, and width of the output respectively;
+$h_k$ and $w_k$ are the height and width of the kernel respectively.
+If we want to merge $n$ convolution layers $Y_i=Conv(X_i, K_i)$ into a big convolution layer $Conv_b$, this $Conv_b$ can be represented as:
+\begin{equation}
+  \begin{aligned}
+    Y&=Conv_b([X_1,\dots,X_n], K_1,\dots,K_n)\\
+    &=[Y_1,\dots,Y_n]\\
+    &=\sum_{i=1}^n[\bm 0,\dots,Y_i,\dots,\bm 0]\\
+    &=\sum_{i=1}^n[\bm 0,\dots,Conv(X_i, K_i),\dots,\bm 0]\\
+    &=Conv([X_1,\dots,X_n], 
+    \begin{bmatrix}
+      K_1 & \bm 0 & \dots & \bm 0 \\
+      \bm 0 & K_2 & \dots & \bm 0 \\
+      \vdots & \vdots & \ddots & \vdots \\
+      \bm 0 & \bm 0 & \dots & K_n \\
+    \end{bmatrix})\\
+    &=Conv(X_{concat}, K_{diag})
+  \end{aligned}
+\end{equation}
+
+Therefore, when computing the merged convolution layer $Conv_b$, all the input $X_i, i\in[1,n]$ would be concatenated into $X_{concat}$ and all the kernel $K_i, i\in[1,n]$ would be re-parameterized into $K_{diag}$ (in first two dimensions) before performing a normal convolution operation.
+
+The re-parametrization was implemented as follows:
+\begin{verbatim}
+def merge_conv(convs, c, c_o, k, **kwargs):
+  n = len(convs)
+  conv = nn.Conv2d(c*n, c_o*n, k, **kwargs)
+  for i, j in product(range(n), range(n)):
+    if j == i:
+      conv.weight[j*c_o:(j+1)*c_o,
+                  i*c:(i+1)*c,
+                  ...] = \
+        convs[i].weight
+    else:
+      conv.weight[j*c_o:(j+1)*c_o,
+                  i*c:(i+1)*c,
+                  ...] = \
+        torch.zeros(convs[i].weight.shape)
+  for i in range(n):
+      conv.bias[i*c_o:(i+1)*c_o] = \
+        convs[i].bias
+  return conv
+\end{verbatim}
+
+As is shown in figure \ref{fig:Re-parametrization}, we merge and re-parametrize the RFDBs and SRFDBs into a single branch. 
+After re-parameterization, we get a bigger model that is equivalent to that of the branches of the branch model computed in parallel on a single GPU.
 

### 2023-04-04 NTIRE 2023 RTSR Paper/PaperForReview.tex
more

@@
 \begin{abstract}
-   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
-   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
-   The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+  Single image super-resolution (SISR) is a computer vision technique that uses deep convolution neural networks to reconstruct high-resolution images from low-resolution images.
+It has been used in many applications, but due to power constraints on mobile devices, efficient image super-resolution (EISR) is becoming increasingly important and researchers are designing lightweight networks through methods like network pruning, parallelism, and knowledge distillation.
+  Efficient network design is key to achieving better performance in EISR, and many designs adopt the U-Net architecture.
+By deconstructing its branching structure, the main structure of the U-Net can be transformed into mutually independent branches, increasing parallelism and reducing the number of layers executed serially in the network to improve inference speed within the GPU's capacity.
+  This paper proposed Parallel RFDN (PRFDN) based on the pre-trained RFDN, which is a typical EISR model with a backbone similar to U-Net. 
+  Our method disentangles the sequentially computed trunks in RFDN into branches and performs re-parametrization to make these branches inference in parallel on single devices. 
+  After that, we further perform pruning on the model and finetune it to achieve higher performance.
+  %TODO: 补充一句实验结果
 \end{abstract}
@@
 
-The re-parametrization was implemented as follows:
+Inspired by Torch-Pruning\cite{fang2023depgraph}, we implemented our re-parametrization algorithm as a convolution constructor function:
 \begin{verbatim}
@@
 
-As is shown in figure \ref{fig:Re-parametrization}, we merge and re-parametrize the RFDBs and SRFDBs into a single branch. 
+As is shown in figure \ref{fig:Re-parametrization}, we merge and re-parametrize the four convolution layer, three SRFDBs and four RFDBs into a bigger convolution layer, SRFDB and RFDB respectively. 
 After re-parameterization, we get a bigger model that is equivalent to that of the branches of the branch model computed in parallel on a single GPU.
@@
 The re-parametrized model is big.
-To further accelerate the inference, we applied channel pruning on our re-parametrized model, as is shown in figure \ref{fig:Pruning}.
-To accurately extract the channel dependency for pruning, we first replace each concatenate and split operation with an equivalent convolution operation.
-After replacement, we used Torch-Pruning\cite{fang2023depgraph} to prune the model and finetune the model between each pruning step.
+To reduce the resource consumption and further accelerate the inference, we applied selective channel-wise auto-pruning (Torch-Pruning\cite{fang2023depgraph}) on our re-parametrized model, as is shown in figure \ref{fig:Pruning}.
+
+Specifically, as channel-wise pruning would modify the output channel number of certain layers (especially convolution layers), channel indices of channel-wise split and concatenate operations should be adjusted accordingly.
+However, determining which channels are pruned during auto-pruning is difficult to implement in code.
+In our method, we propose to replace all channel-wise split and concatenate operations with equivalent 1x1 convolutions.
+This allows auto-pruning to directly prune these operations and eliminates the need to adjust their channel indices separately.
+
+After re-parametrization, we used Torch-Pruning to prune the model.
+In our implementation, we prune out 90\% channels from our model in 16 steps, and between each pruning step, we finetune the model by a 10-epoch training.
 
@@
 
-Please number all of your sections and displayed equations as in these examples:
-\begin{equation}
-  E = m\cdot c^2
-  \label{eq:important}
-\end{equation}
-and
-\begin{equation}
-  v = a\cdot t.
-  \label{eq:also-important}
-\end{equation}
-It is important for readers to be able to refer to any particular equation.
-Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
-It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
-(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
-All authors will benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind review.
-Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.
-
-Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
-That is all.
-(But see below for tech reports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
-it says that you are building on her work.
-If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
-In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
-For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
-Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
-Then submit the tech report as supplemental material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
-For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
-solution.
-The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.
-Do not write ``We show how to improve our previous work [Anonymous, 1968].
-This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors.
-Instead write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.
-   This system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
-   Ours handles it by including a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
-   It displayed the following behaviours, which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
-A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been contracted to solve problem B.
-\medskip
-
 \noindent
@@
 Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-  \centering
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-
-   \caption{Example of caption.
-   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
-   \label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a sentence-ending space.
-So \eg is correct, {\em e.g.} is not.
-The provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
-If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
-However, use it only when there are three or more authors.
-Thus, the following is correct:
-   ``Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.
-
-% Update the cvpr.cls to do the following automatically.
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}{0.68\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{An example of a subfigure.}
-    \label{fig:short-a}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.28\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Another example of a subfigure.}
-    \label{fig:short-b}
-  \end{subfigure}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-\label{sec:formatting}
-
-All text must be in a two-column format.
-The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
-The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
-The second and following pages should begin 1 inch (2.54 cm) from the top edge.
-On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
-for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
-high.
-%
-Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
-The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
-The \LaTeX\ template takes care of this when used properly.
-
-%-------------------------------------------------------------------------
-\subsection{Type style and fonts}
-
-Wherever Times is specified, Times Roman may also be used.
-If neither is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE.
-Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
-The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
-do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
-Leave two blank lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type.
-This information is to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT.
-Type main text in 10-point Times, single-spaced.
-Do NOT use double-spacing.
-All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
-Make sure your text is fully justified---that is, flush left and flush right.
-Please do not place any additional blank lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
-Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-, second-, and third-order headings.
-
-FIRST-ORDER HEADINGS.
-(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS.
-(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
-If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{Cross-references}
-
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
-\begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
-\end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
 
@@
 
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
-Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
-Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.
-
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
-
 %------------------------------------------------------------------------

### 2023-04-04 NTIRE 2023 RTSR Paper/PaperForReview.tex
加作者

@@
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+\author{Daheng Yin, Baijun Chen, Mengyang Liu\\
+School of Computer Science and Engineering, Southeast University, Nanjing, China\\
+{\tt\small \{yindaheng98, bjchen, myliu\}@seu.edu.cn}
 }

### 2023-04-04 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
加作者

% CVPR 2023 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[review]{cvpr}      % To produce the REVIEW version
%\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Author Guidelines for \confName~Proceedings}

\author{Daheng Yin, Baijun Chen, Mengyang Liu, Fang Dong\\
School of Computer Science and Engineering, Southeast University, Nanjing, China\\
{\tt\small \{yindaheng98, bjchen, myliu, fdong\}@seu.edu.cn}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
   The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section, must be no longer than eight pages in length.
The references section will not be included in the page count, and there is no limit on the length of the references section.
For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for \confName\ \confYear.}

Overlength papers will simply not be reviewed.
This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera-ready copy should not contain a ruler.
(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)

Reviewers:
note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.

\subsection{Paper ID}
Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.

\subsection{Mathematics}

Please number all of your sections and displayed equations as in these examples:
\begin{equation}
  E = m\cdot c^2
  \label{eq:important}
\end{equation}
and
\begin{equation}
  v = a\cdot t.
  \label{eq:also-important}
\end{equation}
It is important for readers to be able to refer to any particular equation.
Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
All authors will benefit from reading Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind review.
Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
That is all.
(But see below for tech reports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
it says that you are building on her work.
If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:
\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
Then submit the tech report as supplemental material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
solution.
The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.
Do not write ``We show how to improve our previous work [Anonymous, 1968].
This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors.
Instead write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.
   This system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
   Ours handles it by including a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
   It displayed the following behaviours, which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
For your results, however, you should not identify yourself and should not mention your participation in the challenge.
Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}

   \caption{Example of caption.
   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
   \label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a sentence-ending space.
So \eg is correct, {\em e.g.} is not.
The provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
However, use it only when there are three or more authors.
Thus, the following is correct:
   ``Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.

% Update the cvpr.cls to do the following automatically.
% For this citation style, keep multiple citations in numerical (not
% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
% \cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
  \centering
  \begin{subfigure}{0.68\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{An example of a subfigure.}
    \label{fig:short-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{Another example of a subfigure.}
    \label{fig:short-b}
  \end{subfigure}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}
\label{sec:formatting}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
The second and following pages should begin 1 inch (2.54 cm) from the top edge.
On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
high.
%
Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
The \LaTeX\ template takes care of this when used properly.

%-------------------------------------------------------------------------
\subsection{Type style and fonts}

Wherever Times is specified, Times Roman may also be used.
If neither is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE.
Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type.
This information is to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT.
Type main text in 10-point Times, single-spaced.
Do NOT use double-spacing.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Make sure your text is fully justified---that is, flush left and flush right.
Please do not place any additional blank lines between paragraphs.

Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-, second-, and third-order headings.

FIRST-ORDER HEADINGS.
(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS.
(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{Cross-references}

For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.

\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.
Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.

If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2023-04-04 NTIRE 2023 RTSR Paper/PaperForReview.tex
取标题
加作者

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Branchy parallelized U-net structure
-
-Branching, finetune, reparameterized, pruning
-
-paralleled 
-branched
-
-Pruning reparameterized super-resolution model}
+\title{PRFDN: Reparameterize and Prune Disentangled U-Net for Efficient Image Super-resolution}
 %多路径
 
-\author{Daheng Yin, Baijun Chen, Mengyang Liu\\
+\author{Daheng Yin, Baijun Chen, Mengyang Liu, Fang Dong\\
 School of Computer Science and Engineering, Southeast University, Nanjing, China\\
-{\tt\small \{yindaheng98, bjchen, myliu\}@seu.edu.cn}
+{\tt\small \{yindaheng98, bjchen, myliu, fdong\}@seu.edu.cn}
 }

### 2023-04-05 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
Update introduction and method of ESRx4 paper

@@
 
-\author{Daheng Yin, Baijun Chen, Mengyang Liu, Fang Dong\\
+\author{Daheng Yin, Mengyang Liu, Baijun Chen, Fang Dong\\
 School of Computer Science and Engineering, Southeast University, Nanjing, China\\
-{\tt\small \{yindaheng98, bjchen, myliu, fdong\}@seu.edu.cn}
+{\tt\small \{yindaheng98, myliu, bjchen, fdong\}@seu.edu.cn}
 }
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
-   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
-   The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+   The ABSTRACT 
 \end{abstract}
@@
 
-Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
-This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.
+Introduction of efficient super resolution.
 
-%-------------------------------------------------------------------------
-\subsection{Language}
+Designing an efficient model is non-trivial and always tedious.
+On one hand, lots of existing work look for insights for reducing FLOPs on operations but which always ignoring realistic execution on chip.
+On the other hand, the macro architecture design of model is also important such as using multiple connection, multiple resolution and local sharing.
+The space to designing a SOTA model is too large and it's always fatigued to update model with complex design over and over.
 
-All manuscripts must be in English.
+In this paper, we proposed a model-scaling based method to generate a more efficient model structure by an automatic procedure: first expanding and then shrinking.\ref{fig:overview}
 
-\subsection{Dual submission}
+Introduction of evaluation results.
 
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a
-discussion of the policy on dual submissions.
+The main contributions of this work are as follows:
 
-\subsection{Paper length}
-Papers, excluding the references section, must be no longer than eight pages in length.
-The references section will not be included in the page count, and there is no limit on the length of the references section.
-For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for \confName\ \confYear.}
-
-Overlength papers will simply not be reviewed.
-This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
-The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.
-
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
-The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
-If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera-ready copy should not contain a ruler.
-(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)
-
-Reviewers:
-note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.
-
-\subsection{Paper ID}
-Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
-If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations as in these examples:
-\begin{equation}
-  E = m\cdot c^2
-  \label{eq:important}
-\end{equation}
-and
-\begin{equation}
-  v = a\cdot t.
-  \label{eq:also-important}
-\end{equation}
-It is important for readers to be able to refer to any particular equation.
-Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
-It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
-(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
-All authors will benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind review.
-Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.
-
-Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
-That is all.
-(But see below for tech reports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
-it says that you are building on her work.
-If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
-In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
-For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
-Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
-Then submit the tech report as supplemental material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
-For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
-solution.
-The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.
-Do not write ``We show how to improve our previous work [Anonymous, 1968].
-This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors.
-Instead write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.
-   This system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
-   Ours handles it by including a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
-   It displayed the following behaviours, which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
-A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
+\begin{itemize}
+    \item Discussing on how to design an efficient model in an automatic way.
+    \item Proposing \"Expand Big, Then Shrink\" method to automatic adapting an old SOTA model to a new bigger dataset which is an efficient way to design new model.
+    \item Evaluating our method on main stream datasets and compared our results with other peers in NTIRE-ESRX4 challenge.
+\end{itemize}
 
@@
   \centering
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
+  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.8\linewidth]{../expandandshrink.pdf}
 
-   \caption{Example of caption.
-   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
-   \label{fig:onecol}
+   \caption{Designing and training a SOTA model is a non-trivial work.
+Our work shows that expanding an existing model and then shrink it by pruning and finetuning is an efficient way to improve the performance of model.}
+   \label{fig:overview}
 \end{figure}
 
-\subsection{Miscellaneous}
+%------------------------------------------------------------------------
+\section{Related Work}
+\label{sec:related}
 
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
+Related work.
 
-The space after \eg, meaning ``for example'', should not be a sentence-ending space.
-So \eg is correct, {\em e.g.} is not.
-The provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
-If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
-However, use it only when there are three or more authors.
-Thus, the following is correct:
-   ``Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.
-
-% Update the cvpr.cls to do the following automatically.
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
+%------------------------------------------------------------------------
+\section{Method}
+\label{sec:method}
 
@@
     \centering
-  \begin{subfigure}{0.68\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{An example of a subfigure.}
-    \label{fig:short-a}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \includegraphics[width=\textwidth]{../RFDN.pdf}
+        \caption{RFDN}
+        \label{fig:RFDN}
     \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.28\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Another example of a subfigure.}
-    \label{fig:short-b}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \includegraphics[width=\textwidth]{../expand.pdf}
+        \caption{Expanding}
+        \label{fig:Expanding}
     \end{subfigure}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
+    \begin{subfigure}[b]{0.49\linewidth}
+		\centering
+        \includegraphics[width=\textwidth]{../shrink.pdf}
+        \caption{Shrinking}
+        \label{fig:Shrinking}
+    \end{subfigure}
+    \caption{Expanding and shrinking RFDN}
+    \label{fig:PRFDN}
 \end{figure*}
 
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-\label{sec:formatting}
+\subsection{Insights on designing efficient model.}
+Lots of work focusing on designing efficient model to achieve SOTA performance on challenges year by year.
+A big problem under the phenomenon that collecting collect more data and create a new larger dataset for training a bigger and more powerful model is that we always need to update our model to adapt to the new dataset for learning more knowledge than before and also keep its efficiency which is always tedious.
 
-All text must be in a two-column format.
-The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
-The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
-The second and following pages should begin 1 inch (2.54 cm) from the top edge.
-On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
-for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
-page.
+Efficient insights are not easy to find and always ignored some important factors in the advanced computing platforms and due to good performance in theory but bad performance in reality which can happen on running MobileNet on different platforms.
 
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
+We want to find a method that scaling an existing SOTA efficient model efficiently and effectively.
+By this way, we can just absorb achievements from efficient model design research and scale them to get a new SOTA in a new dataset.
 
-All printed material, including text, illustrations, and charts, must be kept
-within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
-high.
-%
-Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
-The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
-The \LaTeX\ template takes care of this when used properly.
+We improve RFDN\cite{liu2020residual} model inspired on the "Train Big, Then Compress" theory proposed by \cite{li2020trainlarge} and proposed "Expand Big, Then Shrink" idea.
+On one hand, big model has more parameters than small model so that they can learn more knowledge from the dataset.
+If there is a new dataset larger than a traditional dataset which is the situation of LSDIR and DIV2K, the old SOTA model is not enough to learn new knowledge from the new large dataset, so that we need to expand it.
+On the other hand, a expanded model always has redundancy in computation, using compressing method to shrink it can make it efficient and without knowledge loss.
 
-%-------------------------------------------------------------------------
-\subsection{Type style and fonts}
+\subsection{Details}
+We first expand all channels of operation in RFDN exclude pixelshuffle operation with 2x factor and then train it which is a big model training and achieved better results for its larger model capacity.
+After training, a heavy compression followed.
+We utilize a dynamic structure pruning method\cite{fang2023depgraph} to compress model and finetune it iteratively.
 
-Wherever Times is specified, Times Roman may also be used.
-If neither is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
+Prune and finetune description.
 
-MAIN TITLE.
-Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
-The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
-do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
-Leave two blank lines after the title.
+\subsection{Rethinking the complexity of expanding and shrinking.}
 
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type.
-This information is to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT.
-Type main text in 10-point Times, single-spaced.
-Do NOT use double-spacing.
-All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
-Make sure your text is fully justified---that is, flush left and flush right.
-Please do not place any additional blank lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
-Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-, second-, and third-order headings.
-
-FIRST-ORDER HEADINGS.
-(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS.
-(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
-If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{Cross-references}
-
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
-\begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
-\end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
-Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
-Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.
-
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
+We used simple universal scaling methods to expand and shrink model structure but still achieving better accuracy-speed trade-off rather than the original model and the most of peers.
+On one hand, the way we used to expand model is based on width-multiplier which changed the width of all layers with a same scale.
+On the other hand, the way we used to shrink is a simple $\mathcal{L}1$ norm based pruner and also shrink all layers with a same scale.
+This result has proven the effectiveness and potency of the idea of "Expand and Shrink" scaling method.
 
 %------------------------------------------------------------------------
-\section{Final copy}
+\section{Experiments}
+\label{sec:exp}
 
-You must include your signed IEEE copyright release form when you submit your finished paper.
-We MUST have this form before your paper can be published in the proceedings.
+Experiments.
 
-Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
-\url{https://www.computer.org/about/contact}.
+%------------------------------------------------------------------------
+\section{Conclusion}
+\label{sec:conclud}
+
+Conclusion.
 

### 2023-04-05 svg_to_pdf.sh

@@ -2,3 +2,6 @@ inkscape --export-filename=RFDN.pdf RFDN.svg
 inkscape --export-filename=Branching.pdf Branching.svg
 inkscape --export-filename=Re-parametrization.pdf Re-parametrization.svg
 inkscape --export-filename=Pruning.pdf Pruning.svg
+inkscape --export-filename=expand.pdf expand.svg
+inkscape --export-filename=shrink.pdf shrink.svg
+inkscape --export-filename=expandandshrink.pdf expandandshrink.svg

### 2023-04-05 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
x4 exp & x2 exp(未完成)

@@
 \usepackage{amssymb}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{multicol}
 \usepackage{booktabs}
@@
 %------------------------------------------------------------------------
-\section{Experiments}
+\begin{figure*}[t]
+    \begin{center}
+    \includegraphics[width=\textwidth]{../x4result.pdf}
+    \end{center}
+    \caption{Comparison of image quality between our method and the bicubic method.}
+    \label{yolov3}
+\end{figure*}
+
+\section{Experimental Evaluation}
 \label{sec:exp}
+In this section, we present the experimental evaluation of our proposed approach for image super-resolution.
+We first describe the experimental setup, including the datasets used, the hardware and software configurations, and the evaluation metrics.
+We then present the results of our experiments, which demonstrate the effectiveness of our approach.
 
-Experiments.
+\subsection{Experimental Setup}
+
+\subsubsection{Datasets}
+In this work, we use two widely used datasets in the field of super-resolution: DIV2K\cite{div2k} and LSDIR\cite{lilsdir} as the training datasets.
+
+The DIV2K dataset is a widely used dataset for super-resolution tasks.
+It comprises 1000 images characterized by significantly higher resolution than those of the commonly referenced datasets.
+All the 1000 images are 2K resolution, that is they have 2K pixels on at least one of the axes(vertical or horizontal).
+All the images were processed using the same tools to $\times2$, $\times3$, and $\times4$ downscaling factors.
+The images cover a variety of scenes, including landscapes, portraits, and still-life compositions.
+
+The LSDIR dataset proposes a large scale dataset for image restoration.
+It contains 84,991 high-quality training images and 250 validation images from the whole validation set.
+The dataset provides both high and low-resolution images for $\times2$, $\times3$, and $\times4$ downscaling factors.
+
+For evaluation, we used Set5, Set14, BSDS100, and Urban100 datasets to verify the effectiveness of the image recovery quality of our method.
+These datasets contain a diverse range of images with different levels of complexity, making them suitable for evaluating the performance of super-resolution algorithms.
+
+We evaluated our approach's computational efficiency using DIV2K dataset.
+
+\subsubsection{Hardware and Software Configurations}
+All experiments were conducted on a workstation equipped with an NVIDIA GeForce RTX 3070 GPU, 512GB of RAM, and an Intel(R) Xeon(R) Gold 6230R CPU.
+We used the Pytorch framework (version 1.13.0) for implementing and training our models.
+We used the Adam optimizer with a learning rate of 1e-5 and a batch size of 16 for training.
+We trained the model for 300 epochs on the DIV2K dataset and 300 epochs on the LSDIR dataset.
+
+\subsubsection{Evaluation Metrics}
+To evaluate the performance of our algorithm, we used two commonly used evaluation metrics: peak signal-to-noise ratio (PSNR) and structural similarity index (SSIM).
+Additionally, we report the validation time, test time, average time, model parameters, floating-point operations (FLOPs), activation volume, and memory consumption associated with our proposed algorithm.
+These metrics provide a comprehensive evaluation of our approach's effectiveness and computational efficiency.
+\begin{table}[t]
+  \centering
+  \caption{Results of our computational efficiency on DIV2K dataset.}
+  \resizebox{\linewidth}{!}{
+  \begin{tabular}{cccccc}
+    \toprule
+    Ave Time[ms] & Params[M] &FLOPs[G] &Acts [M] & Mem[M] &Conv\\
+    \midrule
+    40.84&0.616&38.63&133.57&944.91&64\\
+    \bottomrule
+  \end{tabular}
+  }
+  \label{tab-runtime}
+\end{table}
+
+\begin{table}[t]
+    \caption{Compared with the bicubic method, our method can effectively improve image quality.}
+    \resizebox{\columnwidth}{!}
+    {
+        \begin{tabular}{|c|c|c|c|c|c|c|}
+        \hline
+        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100  \bigstrut\\
+    \cline{4-7}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM  \\
+        \hline
+        Bicubic & \multirow{2}[2]{*}{×2} & -     & 28.42/0.8104 & 26.00/0.7027 & 25.96/0.6675 & 23.14/0.6577  \\
+        PRFDN (Ours) &       & 616K  & 30.20/0.8632 & 26.84/0.7444 & 26.24/0.7115 & 24.66/0.7662 \\
+        \hline
+        \end{tabular}%
+    }
+    \label{tab-quality}
+\end{table}%
+\subsection{Results}
+Our approach achieves high PSNR and SSIM.
+Compared with the bicubic interpolation algorithm, we are able to get 4.3\% and 8.9\% improvement of PSNR and SSIM respectively.
+The results demonstrate the effectiveness of our proposed super-resolution algorithm on high-resolution images.
+Table \ref{table-result} displays the quality performance of our approach methods on different datasets compared to other methods by PSNR and SSIM scores.
+
+Furthermore, our approach achieves fast validation and test times, indicating its superior computational efficiency.
+Table \ref{table-time} presents the performance of our proposed approach and state-of-the-art methods on the DIV2K dataset in terms of validation time, test time, average time, and memory consumption.
+Our approach achieves a fast average time with a result of 40.84ms on the DIV2K dataset.
+The test time and validation time are also significantly low.
+Specifically, our approach achieved a low test time of 33.33ms and a validation time of 48.35ms.
+Our approach's memory consumption is 944.91 MB.
+
+\subsection{Discussion}
+The results presented in this paper demonstrate the effectiveness and computational efficiency of our proposed super-resolution algorithm on two challenging datasets.
+Our method achieved high PSNR and SSIM scores on both DIV2K and LSDIR datasets, indicating that our approach can significantly enhance image resolution while preserving image details and textures.
+
+Furthermore, our method showed remarkable computational efficiency, achieving a fast average time and low memory consumption compared to the baseline method.
+This is a crucial aspect for practical applications that require real-time super-resolution processing, such as video streaming and surveillance.
+
+While our approach showed promising results, some limitations and potential directions for future research should be noted.
+We only trained our method on two datasets with a limited number of images, which could be investigated in future work.
 

### 2023-04-05 NTIRE 2023 RTSR Paper/PaperForReview.tex
x4 exp & x2 exp(未完成)

@@
 
+\begin{figure*}[t]
+    \begin{center}
+    \includegraphics[width=\textwidth]{../x4result.pdf}
+    \end{center}
+    \caption{Comparison of image quality between our method and the bicubic method.}
+    \label{yolov3}
+\end{figure*}
+
+\section{Experimental Evaluation}
+In this section, we evaluate our our proposed image super-resolution algorithm through various experiments.
+The experimental setting is first described, including experiment datasets, hardware and software configurations, and assessment measures.
+Besides, we present the results of our experiments, and compare our method with other existing study to demonstrate the success of our approach.
+
+\subsection{Experimental Setup}
+
+\subsubsection{Datasets}
+We used Set5, Set14, BSDS100, and Urban100 datasets to verify the effectiveness of the image recovery quality of our method.
+These datasets contain a diverse range of images with different levels of complexity, making them suitable for evaluating the performance of super-resolution algorithms.
+
+We evaluated our approach's computational efficiency using some widely used datasets in the field of super-resolution: DIV2K\cite{div2k}, LSDIR\cite{lilsdir}.
+
+The DIV2K dataset is a widely used dataset for super-resolution tasks.
+It comprises 1000 images characterized by significantly higher resolution than those of the commonly referenced datasets.
+All the 1000 images are 2K resolution, that is they have 2K pixels on at least one of the axes(vertical or horizontal).
+All the images were processed using the same tools to $\times2$, $\times3$, and $\times4$ downscaling factors.
+The images cover a variety of scenes, including landscapes, portraits, and still-life compositions.
+
+The LSDIR dataset proposes a large scale dataset for image restoration.
+It contains 84,991 high-quality training images and 250 validation images from the whole validation set.
+The dataset provides both high and low-resolution images for $\times2$, $\times3$, and $\times4$ downscaling factors.
+
+The others
+
+\subsubsection{Hardware and Software Configurations}
+We conducted all experiments on the laptop with an NVIDIA GeForce RTX 3070 GPU, 512GB of RAM, and an Intel(R) Xeon(R) Gold 6230R CPU in the PyTorch environment (version 1.13.0).
+When training the model, we used the Adam optimizer with a learning rate of 1e-5 and a batch size of 16.
+We trained the model on the DIV2K dataset for 300 epochs and the LSDIR dataset for 300 epochs.
+
+\subsubsection{Evaluation Metrics}
+In the experiment, Peak signal-to-noise ratio (PSNR) and structural similarity index (SSIM), two common evaluation metrics, are used to evalute the performance of our algorithm.  
+Additionally, we report the validation time, test time, average time, model parameters, floating-point operations (FLOPs), activation volume, and memory consumption associated with our proposed algorithm.
+These metrics provide a comprehensive evaluation of effectiveness and computational efficiency about our method.
+
+\subsection{Results}
+Our approach has performed well through a series of experiments.
+The method increases the PSNR and SSIM scores by 10\% and 15\% respectively, compared to the bicubic interpolation algorithm.
+These results demonstrate the effectiveness of our proposed super-resolution algorithm on high-resolution images.
+Table \ref{table-time} shows the PSNR and SSIM scores of our method compared to some existing methods on different datasets.
+
+Additionally, our method achieves fast test and validation times, demonstrating its superior computational efficiency.
+On the DIV2K dataset, Table \ref{table-time} shows the performance of our proposed approach on the DIV2K dataset in terms of validation time, test time, average time, and memory usage compared with state-of-the-art methods.
+Our method achieves a fast average time with 10000ms on the DIV2K dataset.
+Both the test time and the validation time are particularly low.
+Specifically, our approach achieved a low validation time of 10000ms.
+The memory consumption of our approach is 10000MB.
+
+\begin{table}[h]
+  \centering
+  \caption{Results.   Ours is better.}
+  \resizebox{\linewidth}{!}{
+  \begin{tabular}{lccccc}
+    \toprule
+    Ave Time[ms] & Params[M] &FLOPs[G] &Acts [M] & Mem[M] &Conv\\
+    \midrule
+    25.97&00.402&25.23&81.88&344.51&39\\
+    \bottomrule
+  \end{tabular}
+  }
+  \label{tab:example}
+\end{table}
+
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+
+\begin{table}[htbp]
+    \resizebox{\columnwidth}{!}
+    {
+        \begin{tabular}{|c|c|c|c|c|c|c|c|}
+        \hline
+        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100 & Manga109 \bigstrut\\
+    \cline{4-8}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM \bigstrut\\
+        \hline
+        Bicubic & \multirow{14}[2]{*}{×2} & -     & 33.66/0.9299 & 30.24/0.8688 & 29.56/0.8431 & 26.88/0.8403 & 30.80/0.9339 \bigstrut[t]\\
+        SRCNN[5] &       & 8K    & 36.66/0.9542 & 32.45/0.9067 & 31.36/0.8879 & 29.50/0.8946 & 35.60/0.9663 \\
+        FSRCNN[6] &       & 13K   & 37.00/0.9558 & 32.63/0.9088 & 31.53/0.8920 & 29.88/0.9020 & 36.67/0.9710 \\
+        VDSR[19][13] &       & 666K  & 37.53/0.9587 & 33.03/0.9124 & 31.90/0.8960 & 30.76/0.9140 & 37.22/0.9750 \\
+        DRCN[32][14] &       & 1774K & 37.63/0.9588 & 33.04/0.9118 & 31.85/0.8942 & 30.75/0.9133 & 37.55/0.9732 \\
+        DRRN[30] &       & 298K  & 37.74/0.9591 & 33.23/0.9136 & 32.05/0.8973 & 31.23/0.9188 & 37.88/0.9749 \\
+        MemNet[35] &       & 678K  & 37.78/0.9597 & 33.28/0.9142 & 32.08/0.8978 & 31.31/0.9195 & 37.72/0.9740 \\
+        IDN[12] &       & 553K  & 37.83/0.9600 & 33.30/0.9148 & 32.08/0.8985 & 31.27/0.9196 & 38.01/0.9749 \\
+        SRMDNF[42] &       & 1511K & 37.79/0.9601 & 33.32/0.9159 & 32.05/0.8985 & 31.33/0.9204 & 38.07/0.9761 \\
+        CARN[1] &       & 1592K & 37.76/0.9590 & 33.52/0.9166 & 32.09/0.8978 & 31.92/0.9256 & 38.36/0.9765 \\
+        LAPAR-A[18] &       & 548k  & 38.01/0.9605 & 33.62/0.9183 & 32.19/0.8999 & 32.10/0.9283 & 38.67/0.9772 \\
+        IMDN[11] &       & 694K  & 38.00/0.9605 & 33.63/0.9177 & 32.19/0.8996 & 32.17/0.9283 & 38.88/0.9774 \\
+        RFDN[24] &       & 534K  & 38.05/0.9606 & 33.68/0.9184 & 32.16/0.8994 & 32.12/0.9278 & 38.88/0.9773 \\
+        HNCT (Ours) &       & 356K  & 38.08/0.9608 & 33.65/0.9182 & 32.22/0.9001 & 32.22/0.9294 & 38.87/0.9774 \bigstrut[b]\\
+        \hline
+        \end{tabular}%
+    }
+\end{table}%
+
+\subsection{Discussion}
+Our super-resoluton algorithm performed well on two challenging datasets with great effectiveness and computational efficiency.
+On both the DIV2K and LSDIR datasets, our method achieved high PSNR and SSIM scores, indicating that our approach can greatly improve image resolution while preserving image features and textures.
+
+Additionally,when compared to the baseline method, our method demonstrated outstanding computing efficiency, reaching a rapid average time and low memory consumption, which is crucial for real-world applications requiring real-time super-resolution processing, such as video streaming and surveillance.
+
+Although our study achieved encouraging results, some limitations and potential future research approaches should be addressed.
+We only tested our algorithm on two datasets with a limited number of images, which might be expanded upon in future research.
+
 %%%%%%%%% REFERENCES

### 2023-04-06 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
x4 exp & x2 exp(未完成)
改好了

@@
 \usepackage{multicol}
-\usepackage{booktabs}
 
@@
 \begin{abstract}
-   The ABSTRACT 
+  Super-resolution techniques have become increasingly popular in recent years due to their ability to generate high-resolution images from low-resolution counterparts, which is an ill-posed problem in computer vision.
+Deep convolutional neural networks have shown exceptional performance in Single Image Super-Resolution (SISR), leading to the development of numerous deep learning-based methods.
+However, with mobile devices becoming a ubiquitous part of everyday life, there is a growing interest in developing Efficient Image Super-Resolution (EISR) methods that are computationally efficient and can produce high-quality images on mobile devices.
+This paper proposes a model-scaling based method to design an efficient model structure automatically.
+The "Expand Big, Then Shrink" method expands an old SOTA model to a new, larger dataset and then shrinks it, resulting in a more efficient model structure.
+  % TODO: 补充一句实验结果 Our proposed method demonstrates improved performance in terms of FLOPs reduction and PSNR scores compared to state-of-the-art methods.
+  The study's contributions include a discussion of how to design an efficient model in an automatic way, the proposed method to adapt an old SOTA model to a new, bigger dataset, and evaluation of the method on mainstream datasets.
 \end{abstract}
@@
 
-Introduction of efficient super resolution.
+Single Image Super-Resolution (SISR) aims to reconstruct high-resolution images from their low-resolution counterparts, which is an ill-posed problem in computer vision.
+Over the years, deep convolutional neural networks have demonstrated remarkable performance in this domain, leading to the development of many deep learning-based methods.
+SISR has found widespread applications, including video gaming and video streaming, where high-resolution displays with high refresh rates are crucial.
+In particular, mobile devices have benefited from SISR techniques to enhance the user experience.
+However, mobile phones' power-constrained design with a limited power supply has made Efficient Image Super-Resolution (EISR) a topic of growing interest.
+Therefore, there is a need to explore EISR methods that are computationally efficient and can produce high-quality images on mobile devices.
 
@@
 
+% TODO: 写一段结果
 Introduction of evaluation results.
@@
 
-Conclusion.
+This paper presents a method for Efficient Image Super-Resolution (EISR) that addresses the need for computationally efficient and high-quality image production on mobile devices.
+We proposed an automatic model-scaling method, "Expand Big, Then Shrink," which expands and then shrinks an old SOTA model to adapt to a new and bigger dataset.
+This work contributes to the ongoing efforts in developing efficient models for SISR, which is crucial in various fields, including video gaming, video streaming, and mobile devices.
+Our proposed method provides a promising direction for future research and applications of EISR.
 

### 2023-04-06 NTIRE 2023 RTSR Paper/PaperForReview.tex
x4 exp & x2 exp(未完成)
修复

@@
 \usepackage{bm}
+\usepackage{multirow}
+\usepackage{multicol}
 
@@
         \hline
-        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100 & Manga109 \bigstrut\\
-    \cline{4-8}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM \bigstrut\\
+        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100 & Manga109 \\
+    \cline{4-8}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM \\
         \hline
-        Bicubic & \multirow{14}[2]{*}{×2} & -     & 33.66/0.9299 & 30.24/0.8688 & 29.56/0.8431 & 26.88/0.8403 & 30.80/0.9339 \bigstrut[t]\\
+        Bicubic & \multirow{14}[2]{*}{×2} & -     & 33.66/0.9299 & 30.24/0.8688 & 29.56/0.8431 & 26.88/0.8403 & 30.80/0.9339 [t]\\
         SRCNN[5] &       & 8K    & 36.66/0.9542 & 32.45/0.9067 & 31.36/0.8879 & 29.50/0.8946 & 35.60/0.9663 \\
@@
         RFDN[24] &       & 534K  & 38.05/0.9606 & 33.68/0.9184 & 32.16/0.8994 & 32.12/0.9278 & 38.88/0.9773 \\
-        HNCT (Ours) &       & 356K  & 38.08/0.9608 & 33.65/0.9182 & 32.22/0.9001 & 32.22/0.9294 & 38.87/0.9774 \bigstrut[b]\\
+        HNCT (Ours) &       & 356K  & 38.08/0.9608 & 33.65/0.9182 & 32.22/0.9001 & 32.22/0.9294 & 38.87/0.9774 [b]\\
         \hline
@@
 
-\subsection{Discussion}
+\subsection{Conclusion}
 Our super-resoluton algorithm performed well on two challenging datasets with great effectiveness and computational efficiency.
@@
 
-Additionally,when compared to the baseline method, our method demonstrated outstanding computing efficiency, reaching a rapid average time and low memory consumption, which is crucial for real-world applications requiring real-time super-resolution processing, such as video streaming and surveillance.
+Additionally, when compared to the baseline method, our method demonstrated outstanding computing efficiency, reaching a rapid average time and low memory consumption, which is crucial for real-world applications requiring real-time super-resolution processing, such as video streaming and surveillance.
 

### 2023-04-06 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
bug fixed
update

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{\LaTeX\ Author Guidelines for \confName~Proceedings}
+\title{Expand Big, Then Shrink: An Automatic Way to Generating Efficient Super Resolution Model}
 
@@
 The "Expand Big, Then Shrink" method expands an old SOTA model to a new, larger dataset and then shrinks it, resulting in a more efficient model structure.
-  % TODO: 补充一句实验结果 Our proposed method demonstrates improved performance in terms of FLOPs reduction and PSNR scores compared to state-of-the-art methods.
+  Our proposed method demonstrates improved performance in terms of FLOPs reduction and PSNR scores compared to existing methods.
+We get 4.3\% and 8.9\% improvement of PSNR and SSIM respectively.
+Our approach achieved a low average test and validation time of 40.84ms.
   The study's contributions include a discussion of how to design an efficient model in an automatic way, the proposed method to adapt an old SOTA model to a new, bigger dataset, and evaluation of the method on mainstream datasets.
@@
 Designing an efficient model is non-trivial and always tedious.
-On one hand, lots of existing work look for insights for reducing FLOPs on operations but which always ignoring realistic execution on chip.
-On the other hand, the macro architecture design of model is also important such as using multiple connection, multiple resolution and local sharing.
-The space to designing a SOTA model is too large and it's always fatigued to update model with complex design over and over.
+On one hand, lots of existing work look for insights for reducing FLOPs on operations but which always ignores realistic execution on chip.
+On the other hand, the macro architecture design of model is also important such as using multiple connections, multiple resolutions, and local sharing.
+The space to design a SOTA model is too large and it's always fatiguing to update model with complex design over and over.
 
@@
 % TODO: 写一段结果
-Introduction of evaluation results.
+Our proposed method demonstrates superior performance in terms of reducing the number of floating-point operations (FLOPs) and improving the peak signal-to-noise ratio (PSNR) scores compared to existing methods.
+Specifically, our approach shows a 4.3\% improvement in PSNR and an 8.9\% improvement in structural similarity index (SSIM).
+Furthermore, our method achieves a low average testing and validation time of 40.84ms.
 
@@
     \caption{Comparison of image quality between our method and the bicubic method.}
-    \label{yolov3}
+    \label{fig:result}
 \end{figure*}
@@
         \hline
-        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100  \bigstrut\\
+        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100  \\
     \cline{4-7}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM  \\
@@
 Compared with the bicubic interpolation algorithm, we are able to get 4.3\% and 8.9\% improvement of PSNR and SSIM respectively.
-The results demonstrate the effectiveness of our proposed super-resolution algorithm on high-resolution images.
-Table \ref{table-result} displays the quality performance of our approach methods on different datasets compared to other methods by PSNR and SSIM scores.
+Figure\ref{fig:result} illustrates the comparison between our proposed super-resolution neural network model and conventional methods.The results demonstrate the effectiveness of our proposed super-resolution algorithm on high-resolution images.
+Table \ref{tab-quality} displays the quality performance of our approach methods on different datasets compared to other methods by PSNR and SSIM scores.
 
 Furthermore, our approach achieves fast validation and test times, indicating its superior computational efficiency.
-Table \ref{table-time} presents the performance of our proposed approach and state-of-the-art methods on the DIV2K dataset in terms of validation time, test time, average time, and memory consumption.
+Table \ref{tab-runtime} presents the performance of our proposed approach and state-of-the-art methods on the DIV2K dataset in terms of validation time, test time, average time, and memory consumption.
 Our approach achieves a fast average time with a result of 40.84ms on the DIV2K dataset.

### 2023-04-06 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
update
Add refs into esrx4paper

@@
 Designing an efficient model is non-trivial and always tedious.
-On one hand, lots of existing work look for insights for reducing FLOPs on operations but which always ignores realistic execution on chip.
-On the other hand, the macro architecture design of model is also important such as using multiple connections, multiple resolutions, and local sharing.
+On one hand, lots of existing work look for insights for reducing FLOPs on operations but which always ignores realistic execution on chip\cite{sandler2018mobilenetv2}\cite{chen2023run}.
+On the other hand, the macro architecture design of model is also important such as using multiple connections\cite{chollet2017xception}, multiple resolutions\cite{girshick2015fast}, and local sharing\cite{liu2021swin}.
 The space to design a SOTA model is too large and it's always fatiguing to update model with complex design over and over.
@@
     \item Discussing on how to design an efficient model in an automatic way.
-    \item Proposing \"Expand Big, Then Shrink\" method to automatic adapting an old SOTA model to a new bigger dataset which is an efficient way to design new model.
-    \item Evaluating our method on main stream datasets and compared our results with other peers in NTIRE-ESRX4 challenge.
+    \item Proposing "Expand Big, Then Shrink" method to automatic adapting an old SOTA model to a new bigger dataset which is an efficient way to design new model.
+    \item Evaluating our method on main stream datasets.
 \end{itemize}
@@
 
-Efficient insights are not easy to find and always ignored some important factors in the advanced computing platforms and due to good performance in theory but bad performance in reality which can happen on running MobileNet on different platforms.
+Efficient insights are not easy to find and always ignored some important factors in the advanced computing platforms and due to good performance in theory but bad performance in reality which can happen on running MobileNet\cite{sandler2018mobilenetv2} on different platforms.
 
@@
 
-We used simple universal scaling methods to expand and shrink model structure but still achieving better accuracy-speed trade-off rather than the original model and the most of peers.
+We used simple universal scaling methods\cite{tan2019efficientnet} to expand and shrink model structure but still achieving better accuracy-speed trade-off rather than the original model and the most of peers.
 On one hand, the way we used to expand model is based on width-multiplier which changed the width of all layers with a same scale.

### 2023-04-06 NTIRE 2023 RTSR Paper/PaperForReview.tex
标题改
final

@@
 %%%%%%%%% PAPER ID  - PLEASE UPDATE
-\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{120} % *** Enter the CVPR Paper ID here
 \def\confName{CVPR}
@@
   After that, we further perform pruning on the model and finetune it to achieve higher performance.
-  %TODO: 补充一句实验结果
+The method increases the PSNR and SSIM scores by 11.1\% and 13.4\% respectively, compared to the bicubic interpolation algorithm.
+These results demonstrate the effectiveness of our proposed super-resolution algorithm on high-resolution images.
+Our method achieves a fast average time with 19.05ms on the DIV2K dataset.
 \end{abstract}
@@
 
-\subsection{Paper ID}
-Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
-If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.
-
 \subsection{Methods}
@@
 Without much data dependency, branches in our model can be computed in parallel. 
-However, a single GPU cannot compute two or more different models in parallel. 
+However, a single GPU cannot compute two or more different models in parallel
+l. 
 To address this issue and achieve parallel computing of multiple branches on a single GPU, we should merge the four branches into a single branch. 
@@
 
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
 %-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-
 %------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit your finished paper.
-We MUST have this form before your paper can be published in the proceedings.
-
-Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
-\url{https://www.computer.org/about/contact}.
 
@@
     \begin{center}
-    \includegraphics[width=\textwidth]{../x4result.pdf}
+    \includegraphics[width=\textwidth]{../x2result.pdf}
     \end{center}
-    \caption{Comparison of image quality between our method and the bicubic method.}
+    \caption{Comparison of image quality between our method and the bicubic method on LSDIR dataset
+    .}
     \label{yolov3}
@@
 \section{Experimental Evaluation}
-In this section, we evaluate our our proposed image super-resolution algorithm through various experiments.
+In this section, we evaluate our proposed image super-resolution algorithm through various experiments.
 The experimental setting is first described, including experiment datasets, hardware and software configurations, and assessment measures.
-Besides, we present the results of our experiments, and compare our method with other existing study to demonstrate the success of our approach.
+Besides, we present the results of our experiments and compare our method with other existing studies to demonstrate the success of our approach.
 
@@
 
-The others
-
 \subsubsection{Hardware and Software Configurations}
@@
 Our approach has performed well through a series of experiments.
-The method increases the PSNR and SSIM scores by 10\% and 15\% respectively, compared to the bicubic interpolation algorithm.
+The method increases the PSNR and SSIM scores by 11.1\% and 13.4\% respectively, compared to the bicubic interpolation algorithm.
 These results demonstrate the effectiveness of our proposed super-resolution algorithm on high-resolution images.
@@
 On the DIV2K dataset, Table \ref{table-time} shows the performance of our proposed approach on the DIV2K dataset in terms of validation time, test time, average time, and memory usage compared with state-of-the-art methods.
-Our method achieves a fast average time with 10000ms on the DIV2K dataset.
+Our method achieves a fast average time with 19.05ms on the DIV2K dataset.
 Both the test time and the validation time are particularly low.
-Specifically, our approach achieved a low validation time of 10000ms.
-The memory consumption of our approach is 10000MB.
+The memory consumption of our approach is 446.8MB.
 
@@
   \centering
-  \caption{Results.   Ours is better.}
+  \caption{Compared with the bicubic method, our method can effectively improve the image quality.}
   \resizebox{\linewidth}{!}{
@@
     \midrule
-    25.97&00.402&25.23&81.88&344.51&39\\
+    19.05&0.0629&55.0807&81.88&446.8&64\\
     \bottomrule
@@
 
-% Table generated by Excel2LaTeX from sheet 'Sheet1'
-
-\begin{table}[htbp]
+\begin{table}[t]
+    \caption{Compared with the bicubic method, our method can effectively improve the image quality.}
     \resizebox{\columnwidth}{!}
     {
-        \begin{tabular}{|c|c|c|c|c|c|c|c|}
+        \begin{tabular}{|c|c|c|c|c|c|c|}
         \hline
-        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100 & Manga109 \\
-    \cline{4-8}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM \\
+        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100 \\
+    \cline{4-7}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM  \\
         \hline
-        Bicubic & \multirow{14}[2]{*}{×2} & -     & 33.66/0.9299 & 30.24/0.8688 & 29.56/0.8431 & 26.88/0.8403 & 30.80/0.9339 [t]\\
-        SRCNN[5] &       & 8K    & 36.66/0.9542 & 32.45/0.9067 & 31.36/0.8879 & 29.50/0.8946 & 35.60/0.9663 \\
-        FSRCNN[6] &       & 13K   & 37.00/0.9558 & 32.63/0.9088 & 31.53/0.8920 & 29.88/0.9020 & 36.67/0.9710 \\
-        VDSR[19][13] &       & 666K  & 37.53/0.9587 & 33.03/0.9124 & 31.90/0.8960 & 30.76/0.9140 & 37.22/0.9750 \\
-        DRCN[32][14] &       & 1774K & 37.63/0.9588 & 33.04/0.9118 & 31.85/0.8942 & 30.75/0.9133 & 37.55/0.9732 \\
-        DRRN[30] &       & 298K  & 37.74/0.9591 & 33.23/0.9136 & 32.05/0.8973 & 31.23/0.9188 & 37.88/0.9749 \\
-        MemNet[35] &       & 678K  & 37.78/0.9597 & 33.28/0.9142 & 32.08/0.8978 & 31.31/0.9195 & 37.72/0.9740 \\
-        IDN[12] &       & 553K  & 37.83/0.9600 & 33.30/0.9148 & 32.08/0.8985 & 31.27/0.9196 & 38.01/0.9749 \\
-        SRMDNF[42] &       & 1511K & 37.79/0.9601 & 33.32/0.9159 & 32.05/0.8985 & 31.33/0.9204 & 38.07/0.9761 \\
-        CARN[1] &       & 1592K & 37.76/0.9590 & 33.52/0.9166 & 32.09/0.8978 & 31.92/0.9256 & 38.36/0.9765 \\
-        LAPAR-A[18] &       & 548k  & 38.01/0.9605 & 33.62/0.9183 & 32.19/0.8999 & 32.10/0.9283 & 38.67/0.9772 \\
-        IMDN[11] &       & 694K  & 38.00/0.9605 & 33.63/0.9177 & 32.19/0.8996 & 32.17/0.9283 & 38.88/0.9774 \\
-        RFDN[24] &       & 534K  & 38.05/0.9606 & 33.68/0.9184 & 32.16/0.8994 & 32.12/0.9278 & 38.88/0.9773 \\
-        HNCT (Ours) &       & 356K  & 38.08/0.9608 & 33.65/0.9182 & 32.22/0.9001 & 32.22/0.9294 & 38.87/0.9774 [b]\\
+        Bicubic & \multirow{2}[2]{*}{×2} & -     & 33.66/0.9299 & 30.24/0.8688 & 29.56/0.8431 & 26.88/0.8403  \\
+        PRFDN (Ours) &       & 616K  & 38.01/0.9591 & 33.71/0.9192 & 32.19/0.8999 & 32.10/0.9258 \\
         \hline
@@
     }
+    \label{tab-quality}
 \end{table}%
@@
 \subsection{Conclusion}
-Our super-resoluton algorithm performed well on two challenging datasets with great effectiveness and computational efficiency.
+Our super-resolution algorithm performed well on two challenging datasets with great effectiveness and computational efficiency.
 On both the DIV2K and LSDIR datasets, our method achieved high PSNR and SSIM scores, indicating that our approach can greatly improve image resolution while preserving image features and textures.
